---
title: "B12 sharing manuscript: compiled figures"
output:
  html_notebook:
    toc: true
    toc_float: true
editor_options:
  chunk_output_type: inline
---

This notebook has two parts. Run **1. Preprocessing** once to create standardized,
high-resolution panel assets. Thereafter, any figure subsection in **2. Plotting
and assembly** can be edited and run independently.

```{r setup, include=FALSE}
rmd_path <- normalizePath(
  knitr::current_input(dir = TRUE), winslash = "/", mustWork = TRUE
)
project_dir <- normalizePath(
  file.path(dirname(rmd_path), "..", ".."),
  winslash = "/", mustWork = TRUE
)
if (!file.exists(file.path(project_dir, "R", "compiled_figures", "compiled_figures.Rmd"))) {
  stop("Could not locate the repository root from the R Markdown input path.")
}
knitr::opts_knit$set(root.dir = project_dir)
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)
```

# 1. Preprocessing

## Shared paths and functions

```{r preprocessing-functions}
required_packages <- c(
  "ape", "cowplot", "dplyr", "ggnewscale", "ggplot2", "knitr", "magick", "maps", "patchwork", "tibble", "tidyr"
)
missing_packages <- required_packages[
  !vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)
]
if (length(missing_packages) > 0L) {
  stop(
    "Install the missing package(s) before continuing: ",
    paste(missing_packages, collapse = ", ")
  )
}

processed_dir <- file.path(
  project_dir, "data", "processed", "compiled_figures", "processed_panels"
)
output_dir <- file.path(project_dir, "results", "compiled_figures")
additional_subpanel_dir <- file.path(output_dir, "additional_subpanels")

dir.create(processed_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(additional_subpanel_dir, recursive = TRUE, showWarnings = FALSE)

figure1_data_inputs <- c(
  tree = file.path(
    project_dir, "data", "processed", "gtdbtk_tree_analysis",
    "gtdbtk_bac120_study_genomes_bacillati_pseudomonadati_split_rooted_b12_complete_traits.tree"
  ),
  tip_metadata = file.path(
    project_dir, "data", "processed", "gtdbtk_tree_analysis",
    "gtdbtk_bac120_study_genomes_tip_metadata.csv"
  ),
  strain_summary = file.path(
    project_dir, "data", "processed", "b12_trait_survey",
    "b12_trait_survey_strain_summary.csv"
  )
)

# Figure 1D is the manuscript's one intentionally non-R panel.
figure1_cartoon <- file.path(
  project_dir, "assets", "figure_source", "Figure1D_cartoon.svg"
)

stop_if_missing <- function(paths) {
  missing <- paths[!file.exists(paths)]
  if (length(missing) > 0L) {
    stop("Missing input file(s):\n", paste(missing, collapse = "\n"))
  }
  invisible(paths)
}

# Resize to an exact panel box. The Figure 1 source aspect ratios already match
# their boxes, so this introduces no meaningful deformation and requires no crop.
standardize_panel <- function(input, output, width_px, height_px) {
  image <- magick::image_read(input, density = 400)
  image <- magick::image_background(image, "white", flatten = TRUE)
  image <- magick::image_resize(
    image,
    geometry = sprintf("%dx%d!", width_px, height_px),
    filter = "Lanczos"
  )
  image <- magick::image_strip(image)
  magick::image_write(image, path = output, format = "png", density = "400x400")
  invisible(output)
}
```

## Run the raw-data-to-analysis pipeline

The stages below are executed in isolated environments and in their explicit
dependency order. The KEGG KO list must have been acquired once with
`R/cleaning/download_kegg_ko_mapping.R`; it is not downloaded automatically.

```{r run-production-pipeline, include=FALSE}
pipeline_scripts <- c(
  "R/cleaning/b12_trait_survey_preprocess.R",
  "R/cleaning/b12_release_uptake_death_preprocess.R",
  "R/cleaning/growth_dynamics_b12_methionine_preprocess.R",
  "R/analysis/b12_trait_survey_analysis.R",
  "R/analysis/gtdbtk_tree_analysis.R",
  "R/analysis/growth_dynamics_b12_methionine_analysis.R",
  "R/analysis/b12_release_uptake_death_analysis.R",
  "R/analysis/b12_trait_classification_analysis.R"
)
for (script in pipeline_scripts) {
  script_path <- file.path(project_dir, script)
  if (!file.exists(script_path)) stop("Missing production script: ", script_path)
  sys.source(script_path, envir = new.env(parent = globalenv()), chdir = FALSE)
}
```

## Minimal Figure 1 plotting functions

These functions are the transitive subset of the original figure scripts needed
for Figure 1A–C. They have no dependency on files under `results/` or on the
original scripts.

```{r figure1-plotting-functions}
clean_taxonomy_figure1 <- function(x) {
  x <- as.character(x)
  x[is.na(x) | x == ""] <- "Unassigned"
  x
}

get_descendant_tips_figure1 <- function(tree) {
  n_tips <- length(tree$tip.label)
  children_by_parent <- split(tree$edge[, 2], tree$edge[, 1])

  recurse <- function(node) {
    children <- children_by_parent[[as.character(node)]]
    if (is.null(children)) {
      if (node <= n_tips) return(node)
      return(integer())
    }
    c(
      children[children <= n_tips],
      unlist(lapply(children[children > n_tips], recurse), use.names = FALSE)
    )
  }
  recurse
}

make_tree_plot_data_figure1 <- function(tree, tip_metadata) {
  tip_metadata <- tip_metadata |>
    dplyr::mutate(
      class_taxonomy = clean_taxonomy_figure1(gtdb_class),
      total_b12_gm = as.numeric(total_b12_gm),
      uptake_b12_mean = as.numeric(uptake_b12_mean)
    )

  graphics::plot(tree, direction = "downwards", show.tip.label = FALSE, plot = FALSE)
  layout <- get("last_plot.phylo", envir = ape::.PlotPhyloEnv)
  n_tips <- length(tree$tip.label)
  nodes <- tibble::tibble(
    node = seq_along(layout$xx), x = layout$xx, y = layout$yy
  )
  tips <- tibble::tibble(
    tip_label = tree$tip.label,
    node = seq_along(tree$tip.label),
    x = layout$xx[seq_along(tree$tip.label)]
  )

  tree_y_min <- min(nodes$y, na.rm = TRUE)
  tree_y_max <- max(nodes$y, na.rm = TRUE)
  tree_height <- tree_y_max - tree_y_min
  internal_node_y_min <- min(layout$yy[(n_tips + 1):length(layout$yy)], na.rm = TRUE)
  cladogram_tip_y <- internal_node_y_min - tree_height * 0.04
  layout$yy[seq_along(tree$tip.label)] <- cladogram_tip_y

  tips <- tips |>
    dplyr::left_join(tip_metadata, by = "tip_label") |>
    dplyr::mutate(class_taxonomy = clean_taxonomy_figure1(class_taxonomy))

  edges <- tibble::tibble(
    parent = tree$edge[, 1],
    child = tree$edge[, 2],
    parent_x = layout$xx[parent],
    parent_y = layout$yy[parent],
    child_x = layout$xx[child],
    child_y = layout$yy[child]
  )

  descendant_tips <- get_descendant_tips_figure1(tree)
  tip_class_by_node <- stats::setNames(tips$class_taxonomy, tips$node)
  edges <- edges |>
    dplyr::mutate(
      branch_class = vapply(
        child,
        function(child_node) {
          classes <- unique(
            tip_class_by_node[as.character(descendant_tips(child_node))]
          )
          classes <- classes[!is.na(classes) & classes != ""]
          if (length(classes) == 1L) classes else "Mixed"
        },
        character(1)
      )
    )

  list(
    tree = tree,
    tips = tips,
    edges = edges,
    tree_height = tree_height,
    tree_y_max = tree_y_max,
    cladogram_tip_y = cladogram_tip_y
  )
}

make_panel_a_figure1 <- function(plot_data, taxonomy_colors) {
  tips <- plot_data$tips |>
    dplyr::mutate(
      tree_x = plot_data$tree_y_max - plot_data$cladogram_tip_y,
      tree_y = x
    )
  edges <- plot_data$edges |>
    dplyr::rename(
      old_parent_x = parent_x,
      old_parent_y = parent_y,
      old_child_x = child_x,
      old_child_y = child_y
    ) |>
    dplyr::transmute(
      parent_x = plot_data$tree_y_max - old_parent_y,
      parent_y = old_parent_x,
      child_x = plot_data$tree_y_max - old_child_y,
      child_y = old_child_x,
      branch_class
    )

  tree_x_max <- max(tips$tree_x, na.rm = TRUE)
  tree_width <- max(tree_x_max, diff(range(edges$parent_x, na.rm = TRUE)))
  tile_width <- tree_width * 0.066
  tile_gap <- tile_width * 0.22
  total_x <- tree_x_max + tile_gap + tile_width / 2
  uptake_x <- total_x + tile_width + tile_gap
  label_y <- max(tips$tree_y, na.rm = TRUE) + 2.2

  ggplot2::ggplot() +
    ggplot2::theme_void(base_size = 9) +
    ggplot2::coord_cartesian(
      xlim = c(min(edges$parent_x, na.rm = TRUE), uptake_x + tree_width * 0.045),
      ylim = c(min(tips$tree_y, na.rm = TRUE) - 1, label_y + 0.8),
      clip = "off"
    ) +
    ggplot2::scale_x_continuous(
      breaks = c(total_x, uptake_x),
      labels = c("Total B12", "B12 uptake"),
      position = "bottom"
    ) +
    ggplot2::scale_y_continuous(expand = ggplot2::expansion(mult = 0, add = 0)) +
    ggplot2::geom_segment(
      data = edges,
      ggplot2::aes(x = parent_x, xend = parent_x, y = parent_y, yend = child_y,
                   color = branch_class),
      linewidth = 0.42
    ) +
    ggplot2::geom_segment(
      data = edges,
      ggplot2::aes(x = parent_x, xend = child_x, y = child_y, yend = child_y,
                   color = branch_class),
      linewidth = 0.42
    ) +
    ggplot2::scale_color_manual(
      values = taxonomy_colors, breaks = names(taxonomy_colors),
      limits = names(taxonomy_colors), drop = FALSE, name = "GTDB-Tk class",
      na.value = "grey65",
      guide = ggplot2::guide_legend(
        order = 3,
        override.aes = list(linewidth = 0.936, color = unname(taxonomy_colors))
      )
    ) +
    ggnewscale::new_scale_fill() +
    ggplot2::geom_tile(
      data = tips, ggplot2::aes(x = total_x, y = tree_y, fill = total_b12_gm),
      width = tile_width, height = 0.95
    ) +
    ggplot2::scale_fill_gradientn(
      colors = c("#f7fbff", "#6baed6", "#08519c"), trans = "log10",
      limits = c(5, 2000), breaks = c(10, 100, 1000),
      labels = c("10", "100", "1000"), na.value = "grey90",
      name = "Total B12 (pM)", guide = ggplot2::guide_colorbar(order = 1)
    ) +
    ggnewscale::new_scale_fill() +
    ggplot2::geom_tile(
      data = tips, ggplot2::aes(x = uptake_x, y = tree_y, fill = uptake_b12_mean),
      width = tile_width, height = 0.95
    ) +
    ggplot2::scale_fill_gradient2(
      low = "#2166ac", mid = "white", high = "#b2182b", midpoint = 0,
      na.value = "grey90", name = "B12 uptake (pM)",
      guide = ggplot2::guide_colorbar(order = 2)
    ) +
    ggplot2::theme(
      legend.position = c(0.02, 0.02), legend.justification = c(0, 0),
      legend.box = "vertical", legend.box.just = "left",
      legend.title = ggplot2::element_text(size = 11.52, hjust = 0),
      legend.text = ggplot2::element_text(size = 10.08, hjust = 0),
      legend.key.height = grid::unit(0.4608, "cm"),
      legend.spacing.y = grid::unit(0.08, "cm"),
      axis.text.x = ggplot2::element_text(angle = 45, hjust = 1, vjust = 1),
      axis.ticks.x = ggplot2::element_blank(), axis.title.x = ggplot2::element_blank(),
      legend.background = ggplot2::element_rect(fill = "white", color = NA),
      plot.background = ggplot2::element_rect(fill = "white", color = NA),
      plot.margin = ggplot2::margin(8, 8, 8, 8)
    )
}

density_layer_figure1 <- function() {
  ggplot2::stat_density_2d_filled(
    contour_var = "ndensity",
    breaks = c(0, 0.025, 0.05, 0.1, 0.2, 0.3, 0.4, 0.7, 1),
    alpha = 0.5
  )
}

make_panel_b_figure1 <- function(strain_summary) {
  data <- strain_summary |>
    dplyr::filter(
      n_samples >= 3, is.finite(total_b12_gm), total_b12_gm > 0,
      is.finite(total_b12_gsd), total_b12_gsd > 0,
      is.finite(uptake_b12_mean)
    )
  set.seed(610)
  data <- data |>
    dplyr::mutate(
      total_b12_gm_plot = dplyr::if_else(
        total_b12_prop_hit_lower == 1,
        pmax(total_b12_gm + stats::runif(dplyr::n(), -1, 1), .Machine$double.eps),
        total_b12_gm
      )
    )
  labels <- data.frame(
    text = c("Bystander", "Scavenger", "Reclaimer", "Non-Reclaimer"),
    x = c(5, 5, 400, 400), y = c(-200, 700, 700, -200)
  )

  plot <- ggplot2::ggplot(data, ggplot2::aes(total_b12_gm_plot, uptake_b12_mean)) +
    density_layer_figure1() +
    ggplot2::geom_errorbar(
      ggplot2::aes(ymin = uptake_b12_mean - uptake_b12_sd,
                   ymax = uptake_b12_mean + uptake_b12_sd),
      alpha = 0.08, linewidth = 0.4
    ) +
    ggplot2::geom_errorbar(
      ggplot2::aes(xmin = total_b12_gm / total_b12_gsd,
                   xmax = total_b12_gm * total_b12_gsd),
      orientation = "y", alpha = 0.08, linewidth = 0.4
    ) +
    ggplot2::geom_point(color = "black", alpha = 0.7, size = 3) +
    ggplot2::scale_x_log10(limits = c(1, 2000), expand = c(0, 0)) +
    ggplot2::scale_y_continuous(
      breaks = c(-250, 0, 250, 500, 750), limits = c(-250, 750), expand = c(0, 0)
    ) +
    ggplot2::theme_bw(base_size = 13) +
    ggplot2::coord_cartesian(ylim = c(-250, 750), expand = FALSE) +
    ggplot2::labs(x = "Total B12 synthesis (pM)", y = "B12 uptake from 500pM") +
    ggplot2::guides(fill = "none", color = "none") +
    ggplot2::geom_hline(yintercept = 250, linetype = "dashed", colour = "grey40") +
    ggplot2::geom_vline(xintercept = 50, linetype = "dashed", colour = "grey40") +
    ggplot2::geom_text(
      data = labels, ggplot2::aes(x = x, y = y, label = text),
      inherit.aes = FALSE, size = 4.8
    )
  list(plot = plot, data = data)
}

make_panel_c_figure1 <- function(strain_summary) {
  data <- strain_summary |>
    dplyr::filter(
      n_samples >= 3, is.finite(total_b12_gm), total_b12_gm > 50,
      is.finite(filtrate_proportion_gm), filtrate_proportion_gm > 0,
      is.finite(filtrate_proportion_gsd), filtrate_proportion_gsd > 0,
      is.finite(dead_proportion_gm), dead_proportion_gm > 0,
      is.finite(uptake_b12_mean)
    )
  labels <- data.frame(
    text = c("Retainer", "Provider", "Reclaimer"),
    x = c(0.005, 0.8, 0.05), y = c(-200, -200, 700)
  )

  plot <- ggplot2::ggplot(data, ggplot2::aes(filtrate_proportion_gm, uptake_b12_mean)) +
    density_layer_figure1() +
    ggplot2::geom_errorbar(
      ggplot2::aes(ymin = uptake_b12_mean - uptake_b12_sd,
                   ymax = uptake_b12_mean + uptake_b12_sd),
      alpha = 0.1, linewidth = 0.4
    ) +
    ggplot2::geom_errorbar(
      ggplot2::aes(xmin = filtrate_proportion_gm / filtrate_proportion_gsd,
                   xmax = filtrate_proportion_gm * filtrate_proportion_gsd),
      orientation = "y", alpha = 0.1, linewidth = 0.4
    ) +
    ggplot2::geom_point(alpha = 0.65, size = 3, color = "black") +
    ggplot2::scale_x_log10(limits = c(0.001, 2), expand = c(0, 0)) +
    ggplot2::scale_y_continuous(
      breaks = c(-250, 0, 250, 500, 750), limits = c(-250, 750), expand = c(0, 0)
    ) +
    ggplot2::theme_bw(base_size = 13) +
    ggplot2::coord_cartesian(ylim = c(-250, 750), expand = FALSE) +
    ggplot2::labs(x = "Extracellular B12 fraction", y = "B12 uptake from 500pM") +
    ggplot2::guides(fill = "none") +
    ggplot2::geom_hline(yintercept = 250, linetype = "dashed", colour = "grey40") +
    ggplot2::geom_segment(
      data = data.frame(x = 0.05, xend = 0.05, y = -250, yend = 250),
      ggplot2::aes(x = x, xend = xend, y = y, yend = yend),
      inherit.aes = FALSE, linetype = "dashed", colour = "grey40"
    ) +
    ggplot2::geom_text(
      data = labels, ggplot2::aes(x = x, y = y, label = text),
      inherit.aes = FALSE, size = 4.8
    )
  list(plot = plot, data = data)
}
```

## Preprocess Figure 1 panels

The final canvas is 2840 × 3464 px: 7.1 × 8.66 inches at 400 dpi. Panel A is
1299 × 3464 px; panels B and C are 1541 × 1155 px, and D is 1541 × 1154 px.
These dimensions enforce the manuscript-wide maximum width and height.

```{r preprocess-figure1}
stop_if_missing(c(figure1_data_inputs, figure1_cartoon))

figure1_boxes <- list(
  A = c(width = 1299L, height = 3464L),
  B = c(width = 1541L, height = 1155L),
  C = c(width = 1541L, height = 1155L),
  D = c(width = 1541L, height = 1154L)
)

figure1_processed <- file.path(processed_dir, paste0("Figure1", LETTERS[1:4], ".png"))
names(figure1_processed) <- LETTERS[1:4]
figure1_raw_panels <- file.path(processed_dir, paste0("Figure1", LETTERS[1:3], "_raw.png"))
names(figure1_raw_panels) <- LETTERS[1:3]

tree <- ape::read.tree(figure1_data_inputs[["tree"]])
tip_metadata <- utils::read.csv(
  figure1_data_inputs[["tip_metadata"]], check.names = FALSE,
  stringsAsFactors = FALSE, na.strings = c("", "NA")
)
strain_summary <- utils::read.csv(
  figure1_data_inputs[["strain_summary"]], check.names = FALSE,
  stringsAsFactors = FALSE, na.strings = c("", "NA")
)

# Shared strain/taxonomy objects used by Figure 1 and Figures S3-S5. The tree,
# tip metadata, and phenotype summary are each read exactly once above.
gtdb_class_levels <- sort(unique(clean_taxonomy_figure1(tip_metadata$gtdb_class)))
gtdb_class_levels <- c(
  setdiff(gtdb_class_levels, c("Mixed", "Unassigned")),
  intersect(gtdb_class_levels, "Mixed"),
  intersect(gtdb_class_levels, "Unassigned")
)
gtdb_class_palette <- c(
  "#1b9e77", "#d95f02", "#7570b3", "#e7298a", "#66a61e",
  "#e6ab02", "#a6761d", "#1f78b4", "#b2df8a", "#fb9a99",
  "#6a3d9a", "#ff7f00", "#8dd3c7", "#bebada", "#fb8072",
  "#80b1d3", "#fdb462", "#b3de69", "#fccde5", "#bc80bd"
)
gtdb_class_colors <- stats::setNames(
  rep(gtdb_class_palette, length.out = length(gtdb_class_levels)),
  gtdb_class_levels
)
gtdb_class_colors["Mixed"] <- "grey65"
gtdb_class_colors["Unassigned"] <- "grey55"

strain_phenotypes <- strain_summary |>
  dplyr::left_join(
    tip_metadata |>
      dplyr::transmute(
        strain_id = tip_label,
        gtdb_phylum,
        gtdb_class = clean_taxonomy_figure1(gtdb_class),
        gtdb_order
      ),
    by = "strain_id"
  ) |>
  dplyr::mutate(gtdb_class = clean_taxonomy_figure1(gtdb_class))

panel_a_data <- make_tree_plot_data_figure1(tree, tip_metadata)
panel_a <- make_panel_a_figure1(panel_a_data, gtdb_class_colors)
panel_b_result <- make_panel_b_figure1(strain_phenotypes)
panel_c_result <- make_panel_c_figure1(strain_phenotypes)
panel_b <- panel_b_result$plot +
  ggplot2::labs(title = "All strains") +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))
panel_c <- panel_c_result$plot +
  ggplot2::labs(title = "B12 synthesizers") +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))

ggplot2::ggsave(figure1_raw_panels[["A"]], panel_a, width = 4.5, height = 12,
                units = "in", dpi = 400, bg = "white")
ggplot2::ggsave(figure1_raw_panels[["B"]], panel_b, width = 5.12, height = 3.84,
                units = "in", dpi = 400, bg = "white")
ggplot2::ggsave(figure1_raw_panels[["C"]], panel_c, width = 5.12, height = 3.84,
                units = "in", dpi = 400, bg = "white")

figure1_panel_inputs <- c(figure1_raw_panels, D = figure1_cartoon)
for (panel in names(figure1_panel_inputs)) {
  standardize_panel(
    input = figure1_panel_inputs[[panel]],
    output = figure1_processed[[panel]],
    width_px = figure1_boxes[[panel]][["width"]],
    height_px = figure1_boxes[[panel]][["height"]]
  )
}

data.frame(
  panel = names(figure1_processed),
  source = unname(figure1_panel_inputs),
  processed = unname(figure1_processed),
  row.names = NULL
)
```

## Preprocess Figures 2–4

Figures 2–4 use exact source-data exports under `data/processed/figure_source_data`.
These are compact data products—not rendered figures—and preserve model-derived
values and representative-strain selections without requiring the original
figure scripts or rerunning model fitting.

```{r preprocess-figures2-4}
figure2_inputs <- c(
  points = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_trait_classification_analysis",
    "01F_classification_accuracy_random_order_block_held_out_uncolored_points_source.csv"
  ),
  pvalues = file.path(
    project_dir, "data", "processed",
    "b12_trait_classification_analysis",
    "null_mean_performance.csv"
  )
)

figure3_inputs <- c(
  A = file.path(
    project_dir, "data", "processed", "figure_source_data", "b12_trait_survey",
    "15B_dead_cell_fraction_vs_ec_b12_fraction_trait_group2_source.csv"
  ),
  B = file.path(
    project_dir, "data", "processed", "figure_source_data", "b12_trait_survey",
    "15C_ec_b12_fraction_over_dead_cell_fraction_vs_uptake_trait_group2_source.csv"
  )
)

figure4_inputs <- c(
  A = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling", "uptake_fit_dynamics_source_01H.csv"
  ),
  B = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling", "fit_parameter_columns_source_03E.csv"
  ),
  C = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling", "dead_fraction_mix_source_04L.csv"
  ),
  D = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling", "empirical_vs_model_auc_source_07J.csv"
  ),
  D_statistics = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling",
    "auc_mae_strain_label_permutation_summary_10A.csv"
  )
)

stop_if_missing(c(figure2_inputs, figure3_inputs, figure4_inputs))

read_figure_csv <- function(path) {
  utils::read.csv(
    path, check.names = FALSE, stringsAsFactors = FALSE,
    na.strings = c("", "NA")
  )
}

figure2_data <- read_figure_csv(figure2_inputs[["points"]]) |>
  dplyr::mutate(
    accuracy_group = factor(
      accuracy_group,
      levels = c("Matched random folds", "Order block held out")
    ),
    accuracy_model_type = factor(
      accuracy_model_type,
      levels = c("Classifier", "Null")
    ),
    dataset_label = factor(
      dataset_label,
      levels = c("All strains", "B12 synthesizers")
    ),
    trait_facet_label = factor(
      trait_facet_label,
      levels = c("B12 synthesis", "B12 uptake", "EC-B12 fraction")
    )
  )

figure2_pvalues <- read_figure_csv(figure2_inputs[["pvalues"]]) |>
  dplyr::filter(split_type %in% c("random_order_matched_fold", "gtdb_order_block_held_out")) |>
  dplyr::mutate(
    dataset_label = factor(
      dplyr::if_else(
        grepl("total_b12_gt50$", trait), "B12 synthesizers", "All strains"
      ),
      levels = c("All strains", "B12 synthesizers")
    ),
    trait_facet_label = factor(
      dplyr::case_when(
        trait == "log10_total_b12_gm_high" ~ "B12 synthesis",
        grepl("uptake_b12_mean", trait) ~ "B12 uptake",
        grepl("filtrate_proportion_gm", trait) ~ "EC-B12 fraction",
        TRUE ~ trait
      ),
      levels = c("B12 synthesis", "B12 uptake", "EC-B12 fraction")
    ),
    x_start = dplyr::if_else(split_type == "random_order_matched_fold", 0.82, 1.82),
    x_end = dplyr::if_else(split_type == "random_order_matched_fold", 1.18, 2.18),
    y = 1.065,
    y_text = 1.095,
    p_label = dplyr::if_else(
      paired_t_test_p_accuracy < 0.001,
      "p < 0.001",
      paste0(
        "p = ", formatC(paired_t_test_p_accuracy, digits = 3, format = "f")
      )
    )
  )

trait_group_levels <- c("retainer", "provider", "reclaimer")
trait_group_colors <- c(
  retainer = "#7570b3", provider = "#e7298a", reclaimer = "#d95f02",
  Unassigned = "grey55"
)

figure3_data <- lapply(figure3_inputs, read_figure_csv)
figure3_data <- lapply(
  figure3_data,
  function(x) dplyr::mutate(
    x,
    b12_trait_group2 = factor(b12_trait_group2, levels = trait_group_levels)
  )
)

format_one_significant_figure <- function(x) {
  vapply(
    x,
    function(value) format(signif(value, 1), scientific = FALSE, trim = TRUE),
    character(1)
  )
}

figure3a_cor <- stats::cor.test(
  log10(figure3_data$A$dead_proportion_gm),
  log10(figure3_data$A$filtrate_proportion_gm),
  method = "pearson"
)
figure3a_annotation <- data.frame(
  dead_proportion_gm = 10^(log10(0.002) + 0.8 * (log10(1) - log10(0.002))),
  filtrate_proportion_gm = Inf,
  label = paste0(
    "Pearson's r = ", formatC(unname(figure3a_cor$estimate), format = "f", digits = 3),
    "\np = ", formatC(figure3a_cor$p.value, format = "f", digits = 3)
  )
)

figure3b_model <- stats::lm(
  log10_extracellular_over_dead ~ uptake_b12_mean,
  data = figure3_data$B
)
figure3b_r <- stats::cor(
  figure3_data$B$uptake_b12_mean,
  figure3_data$B$log10_extracellular_over_dead,
  use = "complete.obs", method = "pearson"
)
figure3b_p <- coef(summary(figure3b_model))["uptake_b12_mean", "Pr(>|t|)"]
figure3b_annotation <- data.frame(
  uptake_b12_mean = -250 + 0.8 * (650 - (-250)),
  extracellular_over_dead = Inf,
  label = paste0(
    "Pearson's r = ", formatC(figure3b_r, format = "f", digits = 3),
    "\np ", if (figure3b_p < 0.001) "< 0.001" else paste0(
      "= ", formatC(figure3b_p, format = "f", digits = 3)
    )
  )
)

figure4_data <- lapply(figure4_inputs, read_figure_csv)
for (panel in c("A", "B", "C")) {
  figure4_data[[panel]]$b12_trait_group2 <- factor(
    figure4_data[[panel]]$b12_trait_group2,
    levels = trait_group_levels
  )
}
figure4_data$D$trait_group2 <- factor(
  figure4_data$D$trait_group2,
  levels = trait_group_levels
)

# Assign strain ordinals alphabetically within each trait group once, then join
# them to every Figure 4 panel. Expected group sizes are 7, 8, and 8.
figure4_strain_ordinals <- figure4_data$B |>
  dplyr::distinct(b12_trait_group2, strain_id) |>
  dplyr::arrange(b12_trait_group2, strain_id) |>
  dplyr::group_by(b12_trait_group2) |>
  dplyr::mutate(trait_group2_strain_ordinal = dplyr::row_number()) |>
  dplyr::ungroup()
stopifnot(identical(
  as.integer(table(figure4_strain_ordinals$b12_trait_group2)[trait_group_levels]),
  c(7L, 8L, 8L)
))
for (panel in LETTERS[1:4]) {
  figure4_data[[panel]] <- figure4_data[[panel]] |>
    dplyr::left_join(
      figure4_strain_ordinals,
      by = c("b12_trait_group2", "strain_id")
    ) |>
    dplyr::mutate(
      trait_group2_strain_label = paste(
        b12_trait_group2, trait_group2_strain_ordinal, sep = " no."
      )
    )
}
figure4_representative_levels <- figure4_data$A |>
  dplyr::distinct(b12_trait_group2, trait_group2_strain_label) |>
  dplyr::arrange(factor(b12_trait_group2, levels = trait_group_levels)) |>
  dplyr::pull(trait_group2_strain_label)
for (panel in c("A", "C")) {
  figure4_data[[panel]]$trait_group2_strain_label <- factor(
    figure4_data[[panel]]$trait_group2_strain_label,
    levels = figure4_representative_levels
  )
}
figure4_data$A <- figure4_data$A |>
  dplyr::mutate(sample_time_hours = sample_time_minute / 60)
```

## Preprocess Figure 5

```{r preprocess-figure5}
figure5_inputs <- c(
  A = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling", "release_uptake_fit_dynamics_source_02K.csv"
  ),
  B = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling", "fit_parameter_columns_source_03O_03P.csv"
  ),
  Bv2 = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling", "fit_parameter_columns_source_03H.csv"
  ),
  Bv2_k = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling", "fit_parameter_columns_source_03C.csv"
  ),
  C = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling", "fit_parameter_columns_source_03N.csv"
  ),
  D = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling",
    "ec_b12_fraction_per_dead_cell_fraction_vs_k_over_r_source_09B.csv"
  ),
  D_statistics = file.path(
    project_dir, "data", "processed", "figure_source_data",
    "b12_release_uptake_death_modeling",
    "ec_b12_fraction_per_dead_cell_fraction_vs_k_over_r_regression_09B.csv"
  )
)
stop_if_missing(figure5_inputs)
figure5_data <- lapply(figure5_inputs, read_figure_csv)

for (panel in LETTERS[1:4]) {
  figure5_data[[panel]]$b12_trait_group2 <- factor(
    figure5_data[[panel]]$b12_trait_group2,
    levels = trait_group_levels
  )
}
figure5_data$Bv2 <- figure5_data$Bv2 |>
  dplyr::mutate(
    b12_trait_group2 = factor(b12_trait_group2, levels = trait_group_levels),
    added_glucose_mM_C_factor = factor(
      added_glucose_mM_C_factor, levels = c("0", "10")
    )
  )
figure5_data$Bv2_k <- figure5_data$Bv2_k |>
  dplyr::mutate(
    b12_trait_group2 = factor(b12_trait_group2, levels = trait_group_levels),
    added_glucose_mM_C_factor = factor(
      added_glucose_mM_C_factor, levels = c("0", "10")
    )
  )

exact_signed_rank_p <- function(difference) {
  difference <- difference[is.finite(difference) & difference != 0]
  absolute_ranks <- rank(abs(difference), ties.method = "average")
  observed_w_plus <- sum(absolute_ranks[difference > 0])
  possible_w_plus <- vapply(
    0:(2^length(absolute_ranks) - 1),
    function(mask) {
      positive <- as.logical(intToBits(mask)[seq_along(absolute_ranks)])
      sum(absolute_ranks[positive])
    },
    numeric(1)
  )
  min(
    1,
    2 * min(
      mean(possible_w_plus <= observed_w_plus),
      mean(possible_w_plus >= observed_w_plus)
    )
  )
}
figure5v2_wilcoxon <- figure5_data$Bv2 |>
  dplyr::select(strain_id, b12_trait_group2, added_glucose_mM_C, estimate) |>
  tidyr::pivot_wider(
    names_from = added_glucose_mM_C,
    values_from = estimate,
    names_prefix = "glucose_"
  ) |>
  dplyr::group_by(b12_trait_group2) |>
  dplyr::summarise(
    p_value = exact_signed_rank_p(glucose_10 - glucose_0),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    p_label = sprintf("p = %.3f", p_value),
    segment_y = 1.50,
    label_y = 1.57
  )

figure5v2_k_paired <- figure5_data$Bv2_k |>
  dplyr::select(strain_id, b12_trait_group2, added_glucose_mM_C, estimate) |>
  tidyr::pivot_wider(
    names_from = added_glucose_mM_C,
    values_from = estimate,
    names_prefix = "glucose_"
  ) |>
  dplyr::filter(
    is.finite(glucose_0), is.finite(glucose_10),
    glucose_0 > 0, glucose_10 > 0
  )

figure5v2_k_statistics <- figure5v2_k_paired |>
  dplyr::group_by(b12_trait_group2) |>
  dplyr::summarise(
    n_strains = dplyr::n(),
    paired_t_p_linear = stats::t.test(glucose_10, glucose_0, paired = TRUE)$p.value,
    paired_t_p_log = stats::t.test(log(glucose_10), log(glucose_0), paired = TRUE)$p.value,
    exact_wilcoxon_p = exact_signed_rank_p(glucose_10 - glucose_0),
    .groups = "drop"
  ) |>
  dplyr::mutate(p_label = sprintf("p = %.3f", exact_wilcoxon_p))

figure5_data$A <- figure5_data$A |>
  dplyr::left_join(
    figure4_strain_ordinals,
    by = c("b12_trait_group2", "strain_id")
  ) |>
  dplyr::mutate(
    trait_group2_strain_label = paste(
      b12_trait_group2, trait_group2_strain_ordinal, sep = " no."
    ),
    sample_time_hours = sample_time_minute / 60
  )
figure5_representative_levels <- figure5_data$A |>
  dplyr::distinct(b12_trait_group2, trait_group2_strain_label) |>
  dplyr::arrange(factor(b12_trait_group2, levels = trait_group_levels)) |>
  dplyr::pull(trait_group2_strain_label)
figure5_data$A$trait_group2_strain_label <- factor(
  figure5_data$A$trait_group2_strain_label,
  levels = figure5_representative_levels
)
figure5_data$A$added_glucose_mM_C_factor <- factor(
  figure5_data$A$added_glucose_mM_C_factor,
  levels = c("0", "10")
)
```

## Preprocess Figure S1

Figure S1 uses the strain metadata table directly for sampling coordinates and
broad environmental categories. GTDB classes are joined from the same GTDB-Tk
tip metadata used for Figure 1.

```{r preprocess-figure-s1}
figure_s1_metadata_input <- file.path(
  project_dir, "data", "raw", "metadata_strains",
  "bacterial_strain_metadata.csv"
)
stop_if_missing(figure_s1_metadata_input)

figure_s1_metadata <- utils::read.csv(
  figure_s1_metadata_input,
  check.names = FALSE,
  stringsAsFactors = FALSE,
  na.strings = c("", "NA")
) |>
  dplyr::mutate(
    longitude_collected = as.numeric(longitude_collected),
    latitude_collected = as.numeric(latitude_collected),
    broad_environment = dplyr::if_else(
      is.na(broad_environment) | broad_environment == "",
      "Unresolved", broad_environment
    )
  )

# Cluster sampling coordinates in an approximately distance-preserving lon/lat
# space. The seed makes the ten-cluster solution reproducible.
figure_s1_coordinate_data <- figure_s1_metadata |>
  dplyr::filter(
    is.finite(longitude_collected),
    is.finite(latitude_collected)
  ) |>
  dplyr::mutate(
    projected_x = longitude_collected * cos(latitude_collected * pi / 180),
    projected_y = latitude_collected
  )

set.seed(1201)
figure_s1_coordinate_clusters <- stats::kmeans(
  figure_s1_coordinate_data |>
    dplyr::select(projected_x, projected_y),
  centers = 10,
  nstart = 100
)
figure_s1_coordinate_data$cluster_id <- figure_s1_coordinate_clusters$cluster

figure_s1_map_data <- figure_s1_coordinate_data |>
  dplyr::group_by(cluster_id) |>
  dplyr::summarise(
    longitude = mean(longitude_collected),
    latitude = mean(latitude_collected),
    n_strains = dplyr::n(),
    .groups = "drop"
  ) |>
  dplyr::arrange(longitude, latitude) |>
  dplyr::mutate(
    cluster_label = paste0("C", dplyr::row_number()),
    in_continental_us = dplyr::between(longitude, -130, -65) &
      dplyr::between(latitude, 24, 50)
  )

figure_s1_class_lookup <- tip_metadata |>
  dplyr::transmute(
    strain_id = tip_label,
    gtdb_class = clean_taxonomy_figure1(gtdb_class)
  ) |>
  dplyr::distinct(strain_id, .keep_all = TRUE)

figure_s1_composition_data <- figure_s1_metadata |>
  dplyr::filter(!strain_id %in% c("blank", "unknown")) |>
  dplyr::left_join(figure_s1_class_lookup, by = "strain_id") |>
  dplyr::mutate(
    gtdb_class = clean_taxonomy_figure1(gtdb_class),
    broad_environment = factor(
      broad_environment,
      levels = c("soil", "freshwater", "marine")
    )
  ) |>
  dplyr::count(broad_environment, gtdb_class, name = "n_strains", .drop = FALSE) |>
  dplyr::filter(n_strains > 0)

utils::write.csv(
  figure_s1_map_data,
  file.path(output_dir, "FigureS1_sampling_location_clusters_source.csv"),
  row.names = FALSE, na = ""
)
utils::write.csv(
  figure_s1_composition_data,
  file.path(output_dir, "FigureS1_environment_by_gtdb_class_source.csv"),
  row.names = FALSE, na = ""
)
```

## Preprocess Figures S2-S5

S3 reuses `tree`, `tip_metadata`, and `panel_a_data`; S4-S5 reuse the single
`strain_phenotypes` table. Thus the GTDB-Tk tree and strain-level B12 phenotype
data are not loaded a second time.

```{r preprocess-figures-s2-s5}
figure_s2_input <- file.path(
  project_dir, "data", "processed", "growth_dynamics_b12_methionine",
  "07A_mean_auc_B0_M0_vs_B10_M0_source.csv"
)
stop_if_missing(figure_s2_input)
figure_s2_data <- read_figure_csv(figure_s2_input)
figure_s2_labels <- dplyr::filter(figure_s2_data, strain_id == "Ecoli_metE")

# S3 is the same complete GTDB-Tk tree object used to generate Figure 1A.
figure_s3_data <- panel_a_data

figure_s4_data <- list(
  A = strain_phenotypes |>
    dplyr::filter(
      n_samples >= 3,
      is.finite(total_b12_gm), total_b12_gm > 50,
      is.finite(filtrate_b12_gm), filtrate_b12_gm > 0
    ),
  B = strain_phenotypes |>
    dplyr::filter(
      n_samples >= 3,
      is.finite(total_b12_gm), total_b12_gm > 50,
      is.finite(filtrate_b12_gm), filtrate_b12_gm > 0,
      is.finite(uptake_b12_mean)
    ),
  C = strain_phenotypes |>
    dplyr::filter(
      n_samples >= 3,
      is.finite(total_b12_gm), total_b12_gm > 50,
      is.finite(filtrate_proportion_gm), filtrate_proportion_gm > 0,
      is.finite(uptake_b12_mean)
    )
)

format_pearson_label <- function(x, y) {
  test <- stats::cor.test(x, y, method = "pearson")
  paste0(
    "Pearson's r = ", formatC(unname(test$estimate), format = "f", digits = 3),
    "\np ", if (test$p.value < 0.001) "< 0.001" else paste0(
      "= ", formatC(test$p.value, format = "f", digits = 3)
    )
  )
}
figure_s4_labels <- c(
  A = format_pearson_label(
    log10(figure_s4_data$A$total_b12_gm),
    log10(figure_s4_data$A$filtrate_b12_gm)
  ),
  B = format_pearson_label(
    figure_s4_data$B$uptake_b12_mean,
    log10(figure_s4_data$B$filtrate_b12_gm)
  ),
  C = format_pearson_label(
    figure_s4_data$C$uptake_b12_mean,
    log10(figure_s4_data$C$filtrate_proportion_gm)
  )
)

# These are exactly the processed phenotype subsets already used in Figure 1B-C.
figure_s5_data <- list(A = panel_b_result$data, B = panel_c_result$data)
```

## Preprocess Figures S6-S13

```{r preprocess-figures-s6-s13}
supplementary_source_dir <- file.path(project_dir, "data", "processed", "figure_source_data")
figure_s6_inputs <- c(
  A = file.path(supplementary_source_dir, "b12_trait_classification_analysis", "02C_gtdbtk_tree_binary_traits_tips_source.csv"),
  B = file.path(supplementary_source_dir, "b12_trait_classification_analysis", "02D_gtdbtk_total_b12_gt50_pruned_tree_binary_traits_tips_source.csv")
)
figure_s7_input <- file.path(supplementary_source_dir, "b12_trait_classification_analysis", "03B_top_10_mean_permutation_feature_importance_random_order_block_sd_source.csv")
figure_s8_input <- file.path(supplementary_source_dir, "b12_trait_classification_analysis", "04C_rf_feature_importance_vs_pyseer_lrt_pvalue_by_phenotype_source.csv")
figure_s9_input <- file.path(supplementary_source_dir, "b12_release_uptake_death", "06F_live_dead_mix_viability_stain_vs_killed_proportion_source_od600_trait_group2_strain_facets_source.csv")
figure_s10_input <- file.path(supplementary_source_dir, "b12_trait_survey", "12D_trait_group2_boxplot_source.csv")
figure_s11_input <- file.path(supplementary_source_dir, "b12_release_uptake_death_modeling", "uptake_fit_dynamics_source_01K.csv")
figure_s12_input <- file.path(supplementary_source_dir, "b12_release_uptake_death_modeling", "dead_fraction_mix_source_04M_04N_04O.csv")
figure_s13_inputs <- c(
  model = file.path(supplementary_source_dir, "b12_release_uptake_death_modeling", "release_uptake_fit_dynamics_source_02A.csv"),
  empirical = file.path(supplementary_source_dir, "b12_release_uptake_death_modeling", "release_uptake_fit_dynamics_source_02O.csv")
)
stop_if_missing(c(figure_s6_inputs, figure_s7_input, figure_s8_input, figure_s9_input, figure_s10_input, figure_s11_input, figure_s12_input, figure_s13_inputs))

figure_s6_data <- lapply(figure_s6_inputs, read_figure_csv)
figure_s6_data <- lapply(figure_s6_data, function(x) {
  # Use the held-out clade assignment from classification preprocessing. This
  # intentionally assigns the lone Enterobacterales tip in panel B to the
  # pooled group, while Enterobacterales remains separate in panel A.
  x$order_taxonomy <- clean_taxonomy_figure1(x$held_out_group)
  x
})
gtdb_order_levels <- sort(unique(clean_taxonomy_figure1(unlist(lapply(figure_s6_data, `[[`, "order_taxonomy")))))
gtdb_order_levels <- c(setdiff(gtdb_order_levels, c("Mixed", "Unassigned")), intersect(gtdb_order_levels, "Mixed"), intersect(gtdb_order_levels, "Unassigned"))
gtdb_order_colors <- stats::setNames(grDevices::hcl.colors(length(gtdb_order_levels), "Dark 3"), gtdb_order_levels)
gtdb_order_colors["Pooled small orders"] <- "black"
gtdb_order_colors["Mixed"] <- "grey65"
gtdb_order_colors["Unassigned"] <- "grey55"

figure_s7_data <- read_figure_csv(figure_s7_input) |>
  dplyr::mutate(
    train_test_split = factor(
      dplyr::recode(
        split_type,
        random_order_matched_fold = "random",
        gtdb_order_block_held_out = "out-of-clade"
      ),
      levels = c("random", "out-of-clade")
    ),
    data_filtering = factor(
      dplyr::if_else(
        grepl("total_b12_gt50$", trait),
        "B12 synthesizers", "All strains"
      ),
      levels = c("All strains", "B12 synthesizers")
    ),
    predicted_phenotype = factor(
      dplyr::case_when(
        trait == "log10_total_b12_gm_high" ~ "B12 synthesis",
        grepl("uptake_b12_mean", trait) ~ "B12 uptake",
        grepl("filtrate_proportion_gm", trait) ~ "Extracellular B12\nfraction",
        TRUE ~ trait
      ),
      levels = c("B12 synthesis", "B12 uptake", "Extracellular B12\nfraction")
    ),
    facet_label = factor(
      paste(train_test_split, data_filtering, predicted_phenotype, sep = "\n"),
      levels = c(
        "random\nAll strains\nB12 synthesis",
        "random\nAll strains\nB12 uptake",
        "random\nB12 synthesizers\nB12 uptake",
        "random\nB12 synthesizers\nExtracellular B12\nfraction",
        "out-of-clade\nAll strains\nB12 synthesis",
        "out-of-clade\nAll strains\nB12 uptake",
        "out-of-clade\nB12 synthesizers\nB12 uptake",
        "out-of-clade\nB12 synthesizers\nExtracellular B12\nfraction"
      )
    )
  )
figure_s8_data <- read_figure_csv(figure_s8_input) |>
  dplyr::mutate(
    phenotype = factor(
      dplyr::recode(
        phenotype,
        b12_uptake_mean = "B12 uptake",
        total_b12_gm = "B12 synthesis"
      ),
      levels = c("B12 uptake", "B12 synthesis")
    )
  )
figure_s9_data <- read_figure_csv(figure_s9_input)
figure_s10_data <- read_figure_csv(figure_s10_input)
figure_s11_data <- read_figure_csv(figure_s11_input)
figure_s12_data <- read_figure_csv(figure_s12_input)
figure_s13_model <- read_figure_csv(figure_s13_inputs[["model"]])
figure_s13_empirical <- read_figure_csv(figure_s13_inputs[["empirical"]])
figure_s13_empirical$added_glucose_mM_C_factor <- factor(
  figure_s13_empirical$added_glucose_mM_C_factor, levels = c(0, 10)
)
figure_s13_model <- figure_s13_model |>
  dplyr::mutate(
    trait_group2 = dplyr::if_else(is.na(b12_trait_group2) | b12_trait_group2 == "", "NA", b12_trait_group2),
    trait_group2_strain_id = paste(trait_group2, strain_id, sep = "_"),
    added_glucose_mM_C_factor = factor(added_glucose_mM_C, levels = c(0, 10))
  )

# Reuse the alphabetical within-trait-group ordinals established for Figure 4.
supplementary_strain_ordinals <- figure4_strain_ordinals |>
  dplyr::transmute(
    strain_id,
    trait_group2 = as.character(b12_trait_group2),
    trait_group2_strain_ordinal
  ) |>
  dplyr::bind_rows(tibble::tibble(
    strain_id = "blank",
    trait_group2 = "blank",
    trait_group2_strain_ordinal = 0L
  ))
supplementary_facet_levels <- supplementary_strain_ordinals |>
  dplyr::arrange(
    factor(trait_group2, levels = trait_group_levels),
    trait_group2_strain_ordinal
  ) |>
  dplyr::mutate(
    trait_group2_strain_label = dplyr::if_else(
      strain_id == "blank", "blank",
      paste(trait_group2, trait_group2_strain_ordinal, sep = " no.")
    )
  ) |>
  dplyr::pull(trait_group2_strain_label)
supplementary_facet_levels <- c(
  "blank", setdiff(supplementary_facet_levels, "blank")
)
for (object_name in c("figure_s9_data", "figure_s11_data", "figure_s12_data", "figure_s13_model", "figure_s13_empirical")) {
  object <- get(object_name)
  if (!"trait_group2" %in% names(object)) {
    object$trait_group2 <- object$b12_trait_group2
  }
  object <- object |>
    dplyr::mutate(
      trait_group2 = dplyr::if_else(
        strain_id == "blank", "blank", as.character(trait_group2)
      )
    ) |>
    dplyr::select(-dplyr::any_of(c("trait_group2_strain_ordinal", "trait_group2_strain_label"))) |>
    dplyr::left_join(
      supplementary_strain_ordinals,
      by = c("strain_id", "trait_group2")
    ) |>
    dplyr::filter(!is.na(trait_group2_strain_ordinal)) |>
    dplyr::mutate(
      trait_group2 = factor(trait_group2, levels = c("blank", trait_group_levels)),
      trait_group2_strain_label = factor(
        dplyr::if_else(
          strain_id == "blank", "blank",
          paste(trait_group2, trait_group2_strain_ordinal, sep = " no.")
        ),
        levels = supplementary_facet_levels
      )
    )
  assign(object_name, object)
}
```

## Preprocess Figure S14

```{r preprocess-figure-s14}
figure_s14_source_dir <- file.path(
  supplementary_source_dir, "b12_release_uptake_death"
)
figure_s14_inputs <- c(
  A = file.path(figure_s14_source_dir, "12G_release_uptake_b12_240min_endpoint_all_strains_b12_0_trait_group2_source.csv"),
  B = file.path(figure_s14_source_dir, "12H_release_uptake_b12_240min_endpoint_all_strains_b12_500_trait_group2_source.csv"),
  C = file.path(figure_s14_source_dir, "12I_release_uptake_adjusted_od600_240min_b12_0_trait_group2_source.csv"),
  D = file.path(figure_s14_source_dir, "12K_release_uptake_adjusted_live_stain_240min_b12_0_trait_group2_log_y_source.csv"),
  E = file.path(figure_s14_source_dir, "09E_filtrate_b12_per_adjusted_live_stain_glucose_10_vs_0_source.csv"),
  F = file.path(figure_s14_source_dir, "09H_filtrate_b12_per_adjusted_live_stain_glucose_10_over_0_by_trait_group2_source.csv")
)
stop_if_missing(figure_s14_inputs)
figure_s14_data <- lapply(figure_s14_inputs, read_figure_csv)

for (panel in names(figure_s14_data)) {
  figure_s14_data[[panel]]$b12_trait_group2 <- factor(
    figure_s14_data[[panel]]$b12_trait_group2,
    levels = trait_group_levels
  )
}
for (panel in c("A", "B", "C", "D")) {
  figure_s14_data[[panel]]$added_glucose_mM_C <- factor(
    figure_s14_data[[panel]]$added_glucose_mM_C,
    levels = c(0, 10)
  )
}
figure_s14_data$E <- figure_s14_data$E |>
  dplyr::filter(!is.na(b12_trait_group2), strain_id != "blank")

make_figure_s14_paired_statistics <- function(dat, value_column, log_y = FALSE) {
  value_column <- rlang::ensym(value_column)
  maximum <- max(dplyr::pull(dat, !!value_column), na.rm = TRUE)

  dat |>
    dplyr::select(
      strain_id, b12_trait_group2, added_glucose_mM_C,
      value = !!value_column
    ) |>
    tidyr::pivot_wider(
      names_from = added_glucose_mM_C,
      values_from = value,
      names_prefix = "glucose_"
    ) |>
    dplyr::filter(
      is.finite(glucose_0), is.finite(glucose_10),
      !log_y | (glucose_0 > 0 & glucose_10 > 0)
    ) |>
    dplyr::group_by(b12_trait_group2) |>
    dplyr::summarise(
      n_strains = dplyr::n(),
      p_value = exact_signed_rank_p(glucose_10 - glucose_0),
      .groups = "drop"
    ) |>
    dplyr::mutate(
      p_label = sprintf("p = %.3f", p_value),
      segment_y = maximum * if (log_y) 1.25 else 1.10,
      label_y = maximum * if (log_y) 1.32 else 1.14,
      upper_y = maximum * if (log_y) 1.75 else 1.25
    )
}

figure_s14_statistics <- list(
  A = make_figure_s14_paired_statistics(figure_s14_data$A, mean_b12),
  B = make_figure_s14_paired_statistics(figure_s14_data$B, mean_b12),
  C = make_figure_s14_paired_statistics(figure_s14_data$C, mean_measurement),
  D = make_figure_s14_paired_statistics(figure_s14_data$D, mean_measurement, log_y = TRUE)
)

figure_s14f_tests <- figure_s14_data$F |>
  dplyr::filter(is.finite(.data$glucose_10_over_0), .data$glucose_10_over_0 > 0) |>
  dplyr::group_by(.data$b12_trait_group2) |>
  dplyr::summarise(
    n_strains = dplyr::n(),
    p_value = exact_signed_rank_p(.data$glucose_10_over_0 - 1),
    annotation_y = max(.data$glucose_10_over_0) * 1.35,
    .groups = "drop"
  ) |>
  dplyr::mutate(p_label = sprintf("p = %.3f", .data$p_value))
```

## Preprocess Figure S15

```{r preprocess-figure-s15}
figure_s15_inputs <- c(
  ko_matrix = file.path(
    project_dir, "data", "raw", "genome_pipeline_nf_core", "ko_count_matrix.tsv"
  ),
  phenotypes = file.path(
    project_dir, "data", "processed", "b12_trait_survey",
    "b12_trait_survey_gwas_phenotypes.csv"
  ),
  tree = file.path(
    project_dir, "data", "processed", "gtdbtk_tree_analysis",
    "gtdbtk_bac120_study_genomes_bacillati_pseudomonadati_split_rooted_b12_complete_traits.tree"
  ),
  pyseer = file.path(
    project_dir, "data", "processed", "b12_trait_classification_analysis",
    "gwa_pyseer_mixed_tree_comparison_all_traits.csv"
  )
)
stop_if_missing(figure_s15_inputs)

figure_s15_candidates <- tibble::tribble(
  ~ko,      ~gene_symbol,
  "K16092", "btuB",
  "K06858", "btuF",
  "K25034", "btuF",
  "K06073", "btuC",
  "K25027", "btuC",
  "K06074", "btuD",
  "K25028", "btuD",
  "K02471", "bacA/bclA",
  "K16927", "cbrT",
  "K01552", "ecfA",
  "K16785", "ecfT"
) |>
  dplyr::mutate(
    display_label = paste0(.data$gene_symbol, " (", .data$ko, ")"),
    display_label = factor(.data$display_label, levels = rev(.data$display_label))
  )

figure_s15_ko <- utils::read.delim(
  figure_s15_inputs[["ko_matrix"]], check.names = FALSE,
  stringsAsFactors = FALSE
) |>
  dplyr::rename(strain_id = genome)
figure_s15_phenotype <- utils::read.csv(
  figure_s15_inputs[["phenotypes"]], check.names = FALSE,
  stringsAsFactors = FALSE, na.strings = c("", "NA")
) |>
  dplyr::select(strain_id, uptake_b12_mean) |>
  dplyr::distinct(.data$strain_id, .keep_all = TRUE)
figure_s15_tree <- ape::read.tree(figure_s15_inputs[["tree"]])

figure_s15_model_data <- figure_s15_ko |>
  dplyr::inner_join(figure_s15_phenotype, by = "strain_id") |>
  dplyr::filter(
    .data$strain_id %in% figure_s15_tree$tip.label,
    is.finite(.data$uptake_b12_mean)
  )

# Test every variable KO in the matrix. Candidate rows are selected only after
# BH adjustment, so the ordinary-regression correction is genome-wide rather
# than restricted to the 11 displayed transporter KOs.
figure_s15_all_kos <- setdiff(names(figure_s15_ko), "strain_id")
figure_s15_lm_results <- dplyr::bind_rows(lapply(figure_s15_all_kos, function(ko) {
  present <- as.integer(figure_s15_model_data[[ko]] > 0)
  if (length(unique(present[!is.na(present)])) < 2L) {
    return(tibble::tibble(ko = ko, beta = NA_real_, raw_p_value = NA_real_))
  }
  fit <- stats::lm(figure_s15_model_data$uptake_b12_mean ~ present)
  coefficient_table <- summary(fit)$coefficients
  tibble::tibble(
    ko = ko,
    beta = unname(coefficient_table["present", "Estimate"]),
    raw_p_value = unname(coefficient_table["present", "Pr(>|t|)"])
  )
})) |>
  dplyr::mutate(
    bh_p_value = stats::p.adjust(.data$raw_p_value, method = "BH"),
    n_tests_in_bh_family = sum(!is.na(.data$raw_p_value))
  )

figure_s15_pyseer <- utils::read.csv(
  figure_s15_inputs[["pyseer"]], check.names = FALSE,
  stringsAsFactors = FALSE, na.strings = c("", "NA")
) |>
  dplyr::filter(.data$trait == "uptake_b12_mean") |>
  dplyr::transmute(
    representative_variant = .data$variant,
    ko = dplyr::coalesce(.data$cluster_variants_with_tree, .data$variant),
    beta = .data$beta_with_tree,
    raw_p_value = .data$lrt.pvalue_with_tree,
    bh_p_value = .data$p_adj_BH_with_tree,
    n_tests_in_bh_family = sum(!is.na(.data$lrt.pvalue_with_tree))
  ) |>
  # Expansion occurs after the genome-wide Pyseer BH correction. Cluster
  # members inherit one test result and are not counted as independent tests.
  tidyr::separate_rows(ko, sep = ",") |>
  dplyr::filter(.data$ko %in% figure_s15_candidates$ko)

figure_s15_data <- dplyr::bind_rows(
  figure_s15_lm_results |>
    dplyr::filter(.data$ko %in% figure_s15_candidates$ko) |>
    dplyr::mutate(
      method = "Ordinary linear regression",
      representative_variant = .data$ko
    ),
  figure_s15_pyseer |>
    dplyr::mutate(method = "Pyseer + population structure")
) |>
  tidyr::complete(
    ko = figure_s15_candidates$ko,
    method = c("Ordinary linear regression", "Pyseer + population structure")
  ) |>
  dplyr::left_join(figure_s15_candidates, by = "ko") |>
  dplyr::mutate(
    method = factor(
      .data$method,
      levels = c("Ordinary linear regression", "Pyseer + population structure")
    ),
    signed_minus_log10_bh_p = dplyr::if_else(
      !is.na(.data$beta) & !is.na(.data$bh_p_value),
      sign(.data$beta) * -log10(.data$bh_p_value),
      NA_real_
    ),
    p_value_label = dplyr::case_when(
      is.na(.data$bh_p_value) ~ "not tested",
      .data$bh_p_value < 0.001 ~ "<0.001",
      TRUE ~ formatC(.data$bh_p_value, format = "f", digits = 3)
    )
  )

utils::write.csv(
  figure_s15_data,
  file.path(output_dir, "FigureS15_source.csv"),
  row.names = FALSE
)
```

## Preprocess Figure S16

```{r preprocess-figure-s16}
figure_s16_input <- file.path(
  project_dir, "data", "raw", "b12_assay_comparison",
  "Ecoli_chlamy_b12_assay_dataset.csv"
)
stop_if_missing(figure_s16_input)

figure_s16_data <- utils::read.csv(
  figure_s16_input, check.names = FALSE, stringsAsFactors = FALSE,
  na.strings = c("", "NA")
) |>
  dplyr::filter(
    (.data$assay_type == "E. coli OD600" & .data$assay_plate_number %in% c(1, 2)) |
      (.data$assay_type == "Chlamy fluorescence" & .data$assay_plate_number %in% c(3, 4)),
    is.finite(.data$b12_conc_ngl),
    .data$b12_conc_ngl > 0
  ) |>
  dplyr::mutate(
    b12_conc_pM = .data$b12_conc_ngl * 1000 / 1355.39,
    added_met_conc_mgl = dplyr::if_else(
      .data$assay_type == "E. coli OD600",
      pmax(.data$met_conc_mgl - 0.037, 0),
      .data$met_conc_mgl
    ),
    added_met_conc_nM = .data$added_met_conc_mgl * 1e6 / 149.21,
    added_met_conc_uM = .data$added_met_conc_nM / 1000,
    bacteria_strain_id = factor(
      .data$bacteria_strain_id,
      levels = c("blank", "HTWP4", "JW50603", "OTU4908")
    )
  )

utils::write.csv(
  figure_s16_data,
  file.path(output_dir, "FigureS16_source.csv"),
  row.names = FALSE
)
```

## Preprocess Figure S17

```{r preprocess-figure-s17}
figure_s17_input <- file.path(
  project_dir, "data", "intermediate", "b12_trait_survey",
  "b12_assay_combined_b12_trait_survey.csv"
)
stop_if_missing(figure_s17_input)

figure_s17_data <- read_figure_csv(figure_s17_input) |>
  dplyr::filter(
    (sample_type == "filtrate" & assay_type == "standard") |
      assay_type == "sample"
  ) |>
  dplyr::filter(
    is.finite(fluorescence), fluorescence > 0
  ) |>
  dplyr::mutate(
    x_plot = dplyr::if_else(
      assay_type == "standard",
      adjusted_b12_conc_pm,
      dplyr::if_else(sample_volume_added == 10, 8000, 50000)
    ),
    sample_type = factor(
      sample_type,
      levels = c("filtrate", "total", "uptake_0hr", "uptake_1hr")
    ),
    standard_bacteria_strain_id = factor(
      standard_bacteria_strain_id,
      levels = c("blank", "HTWP4", "OTU4908", "sic1606")
    ),
    experiment_name = factor(
      experiment_name,
      levels = c("B12_transfer2", "B12_transfer3")
    ),
    measure_time_hours = factor(
      measure_time_hours,
      levels = c(72, 90, 70, 92)
    )
  ) |>
  dplyr::filter(is.finite(x_plot), x_plot > 0)
```

# 2. Plotting and assembly

## Figure 1

This subsection is independently runnable after the preprocessing chunk has
been run once. The named objects below are the main layout controls.

```{r assemble-figure1, fig.width=7.1, fig.height=8.66, out.width="80%"}
figure1_processed <- file.path(
  processed_dir,
  paste0("Figure1", c("A", "B", "C", "D"), ".png")
)
names(figure1_processed) <- c("A", "B", "C", "D")
stop_if_missing(figure1_processed)

# Editable composition controls.
panel_label_size <- 74
panel_label_x <- 28
panel_label_y <- 23
panel_label_font <- "Helvetica"
panel_label_color <- "black"

add_panel_label <- function(image, label) {
  magick::image_annotate(
    image,
    text = label,
    gravity = "northwest",
    location = sprintf("+%d+%d", panel_label_x, panel_label_y),
    size = panel_label_size,
    font = panel_label_font,
    weight = 700,
    color = panel_label_color
  )
}

panels <- lapply(figure1_processed, magick::image_read)

# Scale only the cartoon content to 80%, retaining its original panel box so it
# remains centered in the right column and the D tag stays aligned with A-C.
panel_d_info <- magick::image_info(panels$D)
panel_d_scaled <- magick::image_resize(
  panels$D,
  geometry = sprintf(
    "%dx%d!",
    round(panel_d_info$width * 0.8),
    round(panel_d_info$height * 0.8)
  ),
  filter = "Lanczos"
)
panels$D <- magick::image_composite(
  magick::image_blank(
    width = panel_d_info$width,
    height = panel_d_info$height,
    color = "white"
  ),
  panel_d_scaled,
  gravity = "center"
)
panels <- Map(add_panel_label, panels, names(panels))

right_column <- magick::image_append(
  c(panels$B, panels$C, panels$D),
  stack = TRUE
)
figure1 <- magick::image_append(c(panels$A, right_column), stack = FALSE)

figure1_png <- file.path(output_dir, "Figure1.png")
figure1_pdf <- file.path(output_dir, "Figure1.pdf")

invisible(magick::image_write(
  figure1, path = figure1_png, format = "png", density = "400x400"
))
invisible(magick::image_write(
  figure1, path = figure1_pdf, format = "pdf", density = "400x400"
))
invisible(NULL)
```

```{r figure1-output-summary}
data.frame(
  output = c(figure1_png, figure1_pdf),
  exists = file.exists(c(figure1_png, figure1_pdf)),
  size_bytes = file.info(c(figure1_png, figure1_pdf))$size,
  row.names = NULL
)
```

## Figure 2

```{r assemble-figure2, fig.width=7.1, fig.height=2.7, out.width="100%"}
set.seed(20260819)
figure2 <- ggplot2::ggplot(
  figure2_data,
  ggplot2::aes(x = accuracy_group, y = accuracy, fill = accuracy_model_type)
) +
  ggplot2::geom_boxplot(
    width = 0.62, color = "grey25", linewidth = 0.35,
    outlier.shape = NA, position = ggplot2::position_dodge(width = 0.72)
  ) +
  ggplot2::geom_segment(
    data = figure2_pvalues,
    ggplot2::aes(x = x_start, xend = x_end, y = y, yend = y),
    inherit.aes = FALSE, linewidth = 0.35
  ) +
  ggplot2::geom_segment(
    data = figure2_pvalues,
    ggplot2::aes(x = x_start, xend = x_start, y = y - 0.01, yend = y),
    inherit.aes = FALSE, linewidth = 0.35
  ) +
  ggplot2::geom_segment(
    data = figure2_pvalues,
    ggplot2::aes(x = x_end, xend = x_end, y = y - 0.01, yend = y),
    inherit.aes = FALSE, linewidth = 0.35
  ) +
  ggplot2::geom_text(
    data = figure2_pvalues,
    ggplot2::aes(x = (x_start + x_end) / 2, y = y_text, label = p_label),
    inherit.aes = FALSE, size = 2.7
  ) +
  ggplot2::geom_point(
    ggplot2::aes(group = accuracy_model_type),
    position = ggplot2::position_jitterdodge(
      dodge.width = 0.72, jitter.width = 0.105, jitter.height = 0,
      seed = 20260819
    ),
    color = "black", shape = 16, size = 1.8, alpha = 0.55
  ) +
  ggplot2::scale_fill_manual(
    values = c(Classifier = "#2F6F73", Null = "#6F6F6F"),
    breaks = c("Classifier", "Null"),
    labels = c("Random forest", "Null (Bernoulli)"),
    name = "Prediction method"
  ) +
  ggplot2::facet_wrap(
    ggplot2::vars(dataset_label, trait_facet_label),
    ncol = 4, labeller = ggplot2::label_value
  ) +
  ggplot2::scale_y_continuous(
    limits = c(-0.05, 1.15), breaks = seq(0, 1, 0.2),
    expand = ggplot2::expansion(mult = c(0, 0))
  ) +
  ggplot2::scale_x_discrete(
    labels = c("Matched random folds" = "Random", "Order block held out" = "Out-of-clade")
  ) +
  ggplot2::labs(x = "Evaluation scheme", y = "Classification accuracy") +
  ggplot2::theme_bw(base_size = 10) +
  ggplot2::theme(
    panel.grid.minor = ggplot2::element_blank(), legend.position = "right",
    strip.background = ggplot2::element_rect(fill = "grey92", color = "grey35"),
    strip.text = ggplot2::element_text(face = "bold"),
    axis.text.x = ggplot2::element_text(color = "black", angle = 0, hjust = 0.5),
    axis.text.y = ggplot2::element_text(color = "black")
  )

figure2_png <- file.path(output_dir, "Figure2.png")
figure2_pdf <- file.path(output_dir, "Figure2.pdf")
ggplot2::ggsave(figure2_png, figure2, width = 7.1, height = 2.7, dpi = 400, bg = "white")
ggplot2::ggsave(figure2_pdf, figure2, width = 7.1, height = 2.7, device = grDevices::cairo_pdf)
figure2
```

## Figure 3

Titles are omitted because the guide uses cropped panels. The trait-group
color mapping is shared across both panels and collected into one legend.

```{r assemble-figure3, fig.width=7.1, fig.height=3.0, out.width="100%"}
figure3a <- ggplot2::ggplot(
  figure3_data$A,
  ggplot2::aes(dead_proportion_gm, filtrate_proportion_gm)
) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      ymin = filtrate_proportion_gm / filtrate_proportion_gsd,
      ymax = filtrate_proportion_gm * filtrate_proportion_gsd
    ), alpha = 0.08, linewidth = 0.4
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      xmin = dead_proportion_gm / dead_proportion_gsd,
      xmax = dead_proportion_gm * dead_proportion_gsd
    ), orientation = "y", alpha = 0.08, linewidth = 0.4
  ) +
  ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "grey45") +
  ggplot2::geom_point(
    ggplot2::aes(color = b12_trait_group2), alpha = 0.75, size = 2.2
  ) +
  ggplot2::geom_smooth(
    method = "lm", se = TRUE, linewidth = 0.8,
    colour = "black", fill = "grey70"
  ) +
  ggplot2::scale_color_manual(values = trait_group_colors, breaks = trait_group_levels, name = "Trait group") +
  ggplot2::scale_x_log10(limits = c(0.002, 1)) +
  ggplot2::scale_y_log10(limits = c(0.0015, 1), breaks = c(0.01, 0.1, 1)) +
  ggplot2::geom_text(
    data = figure3a_annotation,
    ggplot2::aes(x = dead_proportion_gm, y = filtrate_proportion_gm, label = label),
    inherit.aes = FALSE, hjust = 1, vjust = 1.1, size = 2.8
  ) +
  ggplot2::labs(x = "Dead cell fraction", y = "Extracellular B12 fraction") +
  ggplot2::theme_bw(base_size = 9) +
  ggplot2::theme(
    plot.title = ggplot2::element_blank(),
    plot.subtitle = ggplot2::element_blank()
  )

figure3b <- ggplot2::ggplot(
  figure3_data$B,
  ggplot2::aes(uptake_b12_mean, extracellular_over_dead)
) +
  ggplot2::geom_hline(yintercept = 1, linetype = "dashed", colour = "grey45") +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      ymin = extracellular_over_dead / extracellular_over_dead_gsd,
      ymax = extracellular_over_dead * extracellular_over_dead_gsd
    ), alpha = 0.1, linewidth = 0.4
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      xmin = uptake_b12_mean - uptake_b12_sd,
      xmax = uptake_b12_mean + uptake_b12_sd
    ), orientation = "y", alpha = 0.1, linewidth = 0.4
  ) +
  ggplot2::geom_point(
    ggplot2::aes(color = b12_trait_group2), alpha = 0.78, size = 2.2
  ) +
  ggplot2::geom_smooth(
    method = "lm", se = TRUE, linewidth = 0.8, colour = "black", fill = "grey70"
  ) +
  ggplot2::geom_text(
    data = figure3b_annotation,
    ggplot2::aes(x = uptake_b12_mean, y = extracellular_over_dead, label = label),
    inherit.aes = FALSE, hjust = 1, vjust = 1.1, size = 2.8
  ) +
  ggplot2::scale_x_continuous(
    limits = c(-250, 650), breaks = c(-250, 0, 250, 500), expand = c(0, 0)
  ) +
  ggplot2::scale_y_log10(
    breaks = c(0.01, 0.1, 1, 10, 100),
    labels = format_one_significant_figure
  ) +
  ggplot2::scale_color_manual(values = trait_group_colors, breaks = trait_group_levels, name = "Trait group") +
  ggplot2::labs(
    x = "B12 uptake from 500pM",
    y = expression(frac("Extracellular B12 fraction", "Dead cell fraction"))
  ) +
  ggplot2::theme_bw(base_size = 9) +
  ggplot2::theme(
    plot.title = ggplot2::element_blank(),
    plot.subtitle = ggplot2::element_blank()
  )

figure3_legend <- cowplot::get_legend(
  figure3b + ggplot2::theme(legend.position = "right")
)
figure3 <- (
  (figure3a + ggplot2::labs(tag = "A") + ggplot2::theme(legend.position = "none")) |
    patchwork::plot_spacer() |
    (figure3b + ggplot2::labs(tag = "B") + ggplot2::theme(legend.position = "none")) |
    patchwork::wrap_elements(full = figure3_legend)
) +
  patchwork::plot_layout(widths = c(1, 0.04, 1, 0.38)) &
  ggplot2::theme(plot.tag = ggplot2::element_text(face = "bold", size = 11))

figure3_png <- file.path(output_dir, "Figure3.png")
figure3_pdf <- file.path(output_dir, "Figure3.pdf")
ggplot2::ggsave(figure3_png, figure3, width = 7.1, height = 3.0, dpi = 400, bg = "white")
ggplot2::ggsave(figure3_pdf, figure3, width = 7.1, height = 3.0, device = grDevices::cairo_pdf)
figure3
```

## Figure 4

```{r assemble-figure4, fig.width=7.1, fig.height=4.0, out.width="100%"}
figure4_theme <- ggplot2::theme_bw(base_size = 8.7) +
  ggplot2::theme(
    panel.grid.minor = ggplot2::element_blank(),
    strip.background = ggplot2::element_rect(fill = "grey95"),
    plot.title = ggplot2::element_blank(),
    plot.subtitle = ggplot2::element_blank(),
    legend.position = "none"
  )

figure4a <- ggplot2::ggplot(
  figure4_data$A,
  ggplot2::aes(x = sample_time_hours, color = b12_trait_group2)
) +
  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = b12_ymin, ymax = b12_ymax, group = strain_id),
    width = 0, alpha = 0.35, linewidth = 0.3
  ) +
  ggplot2::geom_point(
    ggplot2::aes(y = b12_mean, group = strain_id), alpha = 0.72, size = 1.25
  ) +
  ggplot2::geom_line(
    ggplot2::aes(y = model_pred, group = strain_id), linewidth = 0.7, alpha = 0.9
  ) +
  ggplot2::geom_hline(
    yintercept = 500, linetype = "dashed", color = "grey70", linewidth = 0.4
  ) +
  ggplot2::scale_color_manual(values = trait_group_colors, breaks = trait_group_levels) +
  ggplot2::facet_wrap(ggplot2::vars(trait_group2_strain_label), nrow = 1) +
  ggplot2::labs(x = "Time (hours): t", y = "EC-B12: B(t)") +
  figure4_theme

set.seed(20260819)
figure4b <- ggplot2::ggplot(
  figure4_data$B,
  ggplot2::aes(x = b12_trait_group2, y = estimate)
) +
  ggplot2::geom_boxplot(
    fill = "grey92", color = "grey35", outlier.shape = NA, linewidth = 0.45
  ) +
  ggplot2::geom_point(
    ggplot2::aes(color = b12_trait_group2),
    position = ggplot2::position_jitter(width = 0.12, height = 0, seed = 20260819),
    size = 1.6, alpha = 0.85
  ) +
  ggplot2::scale_color_manual(values = trait_group_colors, breaks = trait_group_levels) +
  ggplot2::scale_y_log10() +
  ggplot2::labs(x = "Trait group", y = "uptake rate: k") +
  figure4_theme +
  ggplot2::theme(plot.margin = ggplot2::margin(t = 12, r = 5.5, b = 5.5, l = 5.5))

figure4c <- ggplot2::ggplot(
  figure4_data$C,
  ggplot2::aes(x = killed_proportion, color = b12_trait_group2)
) +
  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = b12_frac_ymin, ymax = b12_frac_ymax, group = strain_id),
    width = 0.015, alpha = 0.35, linewidth = 0.3
  ) +
  ggplot2::geom_point(
    ggplot2::aes(y = b12_frac_mean, group = strain_id), alpha = 0.72, size = 1.25
  ) +
  ggplot2::geom_line(
    ggplot2::aes(y = predicted_b12_frac, group = strain_id), linewidth = 0.7, alpha = 0.9
  ) +
  ggplot2::scale_color_manual(values = trait_group_colors, breaks = trait_group_levels) +
  ggplot2::scale_x_continuous(breaks = c(0, 0.5, 1)) +
  ggplot2::facet_wrap(ggplot2::vars(trait_group2_strain_label), nrow = 1) +
  ggplot2::labs(x = "Fraction killed: f", y = "EC-B12 fraction: B(1,f)/b") +
  figure4_theme

figure4d_range <- range(
  c(figure4_data$D$empirical_auc, figure4_data$D$model_auc), na.rm = TRUE
)
figure4d_pad <- diff(figure4d_range) * 0.04
figure4d_limits <- figure4d_range + c(-figure4d_pad, figure4d_pad)
figure4d_stats <- figure4_data$D_statistics[1, ]
figure4d_label <- sprintf(
  "CCC = %.3f\nMAE = %.3f\nPerm p = %.3f",
  figure4d_stats$concordance_correlation_coefficient,
  figure4d_stats$observed_mae,
  figure4d_stats$permutation_p_value
)

figure4d <- ggplot2::ggplot(
  figure4_data$D,
  ggplot2::aes(x = empirical_auc, y = model_auc, color = trait_group2)
) +
  ggplot2::geom_abline(
    slope = 1, intercept = 0, linetype = "dashed", color = "grey60", linewidth = 0.4
  ) +
  ggplot2::geom_point(size = 1.7, alpha = 0.9) +
  ggplot2::annotate(
    "text", x = figure4d_limits[1], y = figure4d_limits[2],
    label = figure4d_label, hjust = -0.05, vjust = 1.1, size = 2.32, lineheight = 0.9
  ) +
  ggplot2::scale_color_manual(values = trait_group_colors, breaks = trait_group_levels) +
  ggplot2::coord_cartesian(
    xlim = figure4d_limits, ylim = figure4d_limits, expand = FALSE
  ) +
  ggplot2::labs(x = "Empirical AUC", y = "Model AUC") +
  figure4_theme +
  ggplot2::theme(
    plot.margin = ggplot2::margin(t = 12, r = 5.5, b = 5.5, l = 5.5),
    axis.text.x = ggplot2::element_text(angle = 0, hjust = 0.5)
  )

figure4_design <- c(
  patchwork::area(t = 1, l = 1, b = 1, r = 1),
  patchwork::area(t = 1, l = 2, b = 1, r = 2),
  patchwork::area(t = 2, l = 1, b = 2, r = 1),
  patchwork::area(t = 2, l = 2, b = 2, r = 2)
)
figure4 <- figure4a + patchwork::wrap_elements(full = figure4b) +
  figure4c + patchwork::wrap_elements(full = figure4d) +
  patchwork::plot_layout(
    design = figure4_design,
    widths = c(5.0, 2.1),
    heights = c(1, 1)
  ) +
  patchwork::plot_annotation(tag_levels = "A") &
  ggplot2::theme(plot.tag = ggplot2::element_text(face = "bold", size = 12.8))

figure4_png <- file.path(output_dir, "Figure4.png")
figure4_pdf <- file.path(output_dir, "Figure4.pdf")
ggplot2::ggsave(figure4_png, figure4, width = 7.1, height = 4.0, dpi = 400, bg = "white")
ggplot2::ggsave(figure4_pdf, figure4, width = 7.1, height = 4.0, device = grDevices::cairo_pdf)
figure4
```

## Figure 5

The asymmetric design follows the guide: panel A spans the first two columns,
panel B occupies the upper-right column, panel C occupies the lower-left
column, and panel D spans the remaining two lower columns.

```{r assemble-figure5, fig.width=7.1, fig.height=4.59, out.width="100%"}
figure5_theme <- ggplot2::theme_bw(base_size = 8.7) +
  ggplot2::theme(
    panel.grid.minor = ggplot2::element_blank(),
    strip.background = ggplot2::element_rect(fill = "grey95"),
    plot.title = ggplot2::element_blank(),
    plot.subtitle = ggplot2::element_blank()
  )

figure5a <- ggplot2::ggplot(
  figure5_data$A,
  ggplot2::aes(x = sample_time_hours, color = b12_trait_group2)
) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      ymin = b12_ymin, ymax = b12_ymax,
      group = interaction(strain_id, added_glucose_mM_C_factor)
    ),
    width = 0, alpha = 0.3, linewidth = 0.25
  ) +
  ggplot2::geom_point(
    ggplot2::aes(
      y = b12_mean, shape = added_glucose_mM_C_factor,
      group = interaction(strain_id, added_glucose_mM_C_factor)
    ),
    alpha = 0.72, size = 1.15
  ) +
  ggplot2::geom_line(
    ggplot2::aes(
      y = model_pred, linetype = added_glucose_mM_C_factor,
      group = interaction(strain_id, added_glucose_mM_C_factor)
    ),
    linewidth = 0.65, alpha = 0.9
  ) +
  ggplot2::scale_color_manual(values = trait_group_colors, breaks = trait_group_levels) +
  ggplot2::scale_shape_manual(
    name = "Glucose (mM C)", values = c(`0` = 16, `10` = 17)
  ) +
  ggplot2::scale_linetype_manual(
    name = "Glucose (mM C)", values = c(`0` = "solid", `10` = "dashed")
  ) +
  ggplot2::facet_wrap(ggplot2::vars(trait_group2_strain_label), nrow = 1) +
  ggplot2::labs(x = "Time (hours): t", y = "Extracellular B12: B(t)") +
  ggplot2::guides(
    color = "none",
    shape = ggplot2::guide_legend(ncol = 1, byrow = TRUE),
    linetype = ggplot2::guide_legend(ncol = 1, byrow = TRUE)
  ) +
  figure5_theme +
  ggplot2::theme(
    legend.position = "inside",
    legend.position.inside = c(0.02, 0.96),
    legend.justification = c(0, 1),
    legend.direction = "vertical",
    legend.box = "vertical",
    legend.background = ggplot2::element_rect(
      fill = grDevices::adjustcolor("white", alpha.f = 0.82),
      color = "grey70"
    ),
    legend.margin = ggplot2::margin(2, 3, 2, 3),
    legend.key.width = grid::unit(0.7, "lines"),
    legend.key.height = grid::unit(0.7, "lines")
  )

figure5b_limits <- range(
  c(figure5_data$B$r_glucose_0, figure5_data$B$r_glucose_10), na.rm = TRUE
)
figure5b_pad <- diff(figure5b_limits) * 0.05
figure5b_limits <- figure5b_limits + c(-figure5b_pad, figure5b_pad)

figure5b <- ggplot2::ggplot(
  figure5_data$B,
  ggplot2::aes(x = r_glucose_0, y = r_glucose_10, color = b12_trait_group2)
) +
  ggplot2::geom_abline(
    slope = 1, intercept = 0, linetype = "dashed", color = "grey45", linewidth = 0.4
  ) +
  ggplot2::geom_point(size = 1.7, alpha = 0.85) +
  ggplot2::scale_color_manual(values = trait_group_colors, breaks = trait_group_levels) +
  ggplot2::coord_equal(xlim = figure5b_limits, ylim = figure5b_limits) +
  ggplot2::labs(
    x = "release rate: r (no glucose)",
    y = "release rate: r (+ glucose)"
  ) +
  figure5_theme +
  ggplot2::theme(legend.position = "none")

figure5b_v2 <- ggplot2::ggplot(
  figure5_data$Bv2,
  ggplot2::aes(x = added_glucose_mM_C_factor, y = estimate)
) +
  ggplot2::geom_boxplot(
    fill = "grey92", color = "grey35", outlier.shape = NA, linewidth = 0.45
  ) +
  ggplot2::geom_point(
    ggplot2::aes(color = b12_trait_group2),
    position = ggplot2::position_jitter(
      width = 0.12, height = 0, seed = 20260821
    ),
    size = 1.35, alpha = 0.85
  ) +
  ggplot2::geom_segment(
    data = figure5v2_wilcoxon,
    ggplot2::aes(x = 1, xend = 2, y = segment_y, yend = segment_y),
    inherit.aes = FALSE, color = "black", linewidth = 0.4
  ) +
  ggplot2::geom_text(
    data = figure5v2_wilcoxon,
    ggplot2::aes(x = 1.5, y = label_y, label = p_label),
    inherit.aes = FALSE, color = "black", size = 2.5, vjust = 0
  ) +
  ggplot2::scale_color_manual(
    values = trait_group_colors, breaks = trait_group_levels
  ) +
  ggplot2::scale_y_continuous(
    limits = c(-0.05, 1.7), expand = ggplot2::expansion(mult = c(0, 0))
  ) +
  ggplot2::facet_wrap(ggplot2::vars(b12_trait_group2), nrow = 1) +
  ggplot2::labs(
    x = "Added glucose (mM C)", y = "release rate: r",
    title = NULL, subtitle = NULL, color = NULL
  ) +
  figure5_theme +
  ggplot2::theme(
    legend.position = "none",
    strip.text = ggplot2::element_text(size = 6.7)
  )

figure5c <- ggplot2::ggplot(
  figure5_data$C,
  ggplot2::aes(x = k, y = r, color = b12_trait_group2)
) +
  ggplot2::geom_point(size = 1.7, alpha = 0.85) +
  ggplot2::scale_x_log10() +
  ggplot2::scale_y_log10() +
  ggplot2::scale_color_manual(
    values = trait_group_colors, breaks = trait_group_levels,
    name = "Trait group"
  ) +
  ggplot2::labs(x = "uptake rate: k", y = "release rate: r") +
  figure5_theme +
  ggplot2::theme(legend.position = "none", aspect.ratio = 1)

figure5d_stats <- figure5_data$D_statistics[1, ]
figure5d_pearson_r <- sign(figure5d_stats$slope) * sqrt(figure5d_stats$r_squared)
figure5d_label <- sprintf(
  "Pearson's r = %.3f\np = %.3g",
  figure5d_pearson_r,
  figure5d_stats$slope_p_value
)

figure5d <- ggplot2::ggplot(
  figure5_data$D,
  ggplot2::aes(
    x = k_over_r,
    y = ec_b12_fraction_per_dead_cell_fraction,
    color = b12_trait_group2
  )
) +
  ggplot2::geom_hline(
    yintercept = 1, linetype = "dashed", color = "grey45", linewidth = 0.4
  ) +
  ggplot2::geom_smooth(
    ggplot2::aes(group = 1), method = "lm", formula = y ~ x,
    color = "grey35", fill = "grey70", linewidth = 0.8, alpha = 0.25
  ) +
  ggplot2::geom_point(size = 1.7, alpha = 0.85) +
  ggplot2::annotate(
    "text", x = Inf, y = Inf, label = figure5d_label,
    hjust = 1.1, vjust = 1.1, size = 2.55, lineheight = 0.9
  ) +
  ggplot2::scale_x_log10() +
  ggplot2::scale_y_log10() +
  ggplot2::scale_color_manual(
    values = trait_group_colors, breaks = trait_group_levels,
    name = "Trait group"
  ) +
  ggplot2::labs(
    x = "k/r ratio",
    y = expression(frac("Extracellular B12 fraction", "Dead cell fraction"))
  ) +
  figure5_theme +
  ggplot2::theme(legend.position = "right", aspect.ratio = 1)

figure5d_legend <- cowplot::get_legend(figure5d)
figure5d <- figure5d + ggplot2::theme(legend.position = "none")

figure5_top <- (
  (figure5a + ggplot2::labs(tag = "A")) |
    patchwork::wrap_elements(full = figure5b + ggplot2::labs(tag = "B"))
) + patchwork::plot_layout(widths = c(2.2, 1)) &
  ggplot2::theme(plot.margin = ggplot2::margin(t = 5.5, r = 5.5, b = 0, l = 5.5))
figure5_bottom <- (
  (figure5c + ggplot2::labs(tag = "C")) |
    (figure5d + ggplot2::labs(tag = "D")) |
    patchwork::wrap_elements(full = figure5d_legend)
) + patchwork::plot_layout(widths = c(1, 1, 0.42)) &
  ggplot2::theme(plot.margin = ggplot2::margin(t = 0, r = 5.5, b = 5.5, l = 5.5))
figure5 <- (
  patchwork::wrap_elements(full = figure5_top) /
    patchwork::wrap_elements(full = figure5_bottom)
) + patchwork::plot_layout(heights = c(1, 1.2)) &
  ggplot2::theme(plot.tag = ggplot2::element_text(face = "bold", size = 12.8))

figure5v2_top <- (
  (figure5a + ggplot2::labs(tag = "A")) |
    patchwork::wrap_elements(full = figure5b_v2 + ggplot2::labs(tag = "B"))
) + patchwork::plot_layout(widths = c(2.2, 1)) &
  ggplot2::theme(plot.margin = ggplot2::margin(t = 5.5, r = 5.5, b = 0, l = 5.5))
figure5v2 <- (
  patchwork::wrap_elements(full = figure5v2_top) /
    patchwork::wrap_elements(full = figure5_bottom)
) + patchwork::plot_layout(heights = c(1, 1.2)) &
  ggplot2::theme(plot.tag = ggplot2::element_text(face = "bold", size = 12.8))

figure5_png <- file.path(output_dir, "Figure5.png")
figure5_pdf <- file.path(output_dir, "Figure5.pdf")
ggplot2::ggsave(figure5_png, figure5, width = 7.1, height = 4.59, dpi = 400, bg = "white")
ggplot2::ggsave(
  figure5_pdf, figure5, width = 7.1, height = 4.59,
  device = grDevices::cairo_pdf
)
figure5v2_png <- file.path(output_dir, "Figure5v2.png")
figure5v2_pdf <- file.path(output_dir, "Figure5v2.pdf")
ggplot2::ggsave(
  figure5v2_png, figure5v2, width = 7.1, height = 4.59,
  dpi = 400, bg = "white"
)
ggplot2::ggsave(
  figure5v2_pdf, figure5v2, width = 7.1, height = 4.59,
  device = grDevices::cairo_pdf
)
figure5
figure5v2
```

## Additional Figure 5 subpanels

```{r additional-figure5-subpanels, fig.width=3.2, fig.height=2.4, out.width="55%"}
figure5_k_max <- max(figure5_data$Bv2_k$estimate, na.rm = TRUE)
figure5_k_min <- min(figure5_data$Bv2_k$estimate[figure5_data$Bv2_k$estimate > 0], na.rm = TRUE)

figure5v2_k_statistics <- figure5v2_k_statistics |>
  dplyr::mutate(
    segment_y_linear = figure5_k_max * 1.10,
    label_y_linear = figure5_k_max * 1.14,
    segment_y_log = figure5_k_max * 1.25,
    label_y_log = figure5_k_max * 1.20
  )

make_figure5_k_subpanel <- function(log_y = FALSE) {
  p <- ggplot2::ggplot(
    figure5_data$Bv2_k,
    ggplot2::aes(x = added_glucose_mM_C_factor, y = estimate)
  ) +
    ggplot2::geom_boxplot(
      fill = "grey92", color = "grey35", outlier.shape = NA, linewidth = 0.45
    ) +
    ggplot2::geom_line(
      ggplot2::aes(group = strain_id),
      color = "grey45", linewidth = 0.35, alpha = 0.30
    ) +
    ggplot2::geom_point(
      ggplot2::aes(color = b12_trait_group2),
      position = ggplot2::position_jitter(
        width = 0.12, height = 0, seed = 20260821
      ),
      size = 1.35, alpha = 0.85
    ) +
    ggplot2::geom_segment(
      data = figure5v2_k_statistics,
      ggplot2::aes(
        x = 1, xend = 2,
        y = if (log_y) segment_y_log else segment_y_linear,
        yend = if (log_y) segment_y_log else segment_y_linear
      ),
      inherit.aes = FALSE, color = "black", linewidth = 0.4
    ) +
    ggplot2::geom_text(
      data = figure5v2_k_statistics,
      ggplot2::aes(
        x = 1.5,
        y = if (log_y) label_y_log else label_y_linear,
        label = p_label
      ),
      inherit.aes = FALSE, color = "black", size = 2.5,
      vjust = if (log_y) 1.2 else 0
    ) +
    ggplot2::scale_color_manual(
      values = trait_group_colors, breaks = trait_group_levels
    ) +
    ggplot2::facet_wrap(ggplot2::vars(b12_trait_group2), nrow = 1) +
    ggplot2::labs(
      x = "Added glucose (mM C)",
      y = "uptake rate: k",
      title = if (log_y) {
        "Uptake rate by glucose treatment (log scale)"
      } else {
        "Uptake rate by glucose treatment"
      },
      color = NULL
    ) +
    figure5_theme +
    ggplot2::theme(
      legend.position = "none",
      strip.text = ggplot2::element_text(size = 6.7),
      plot.title = ggplot2::element_text(size = 9, face = "bold", hjust = 0.5)
    )

  if (log_y) {
    p +
      ggplot2::scale_y_log10(
        limits = c(figure5_k_min / 1.15, figure5_k_max * 1.40),
        expand = ggplot2::expansion(mult = c(0, 0))
      )
  } else {
    p +
      ggplot2::scale_y_continuous(
        limits = c(0, figure5_k_max * 1.28),
        expand = ggplot2::expansion(mult = c(0, 0))
      )
  }
}

figure5_05_1 <- make_figure5_k_subpanel(log_y = FALSE)
figure5_05_2 <- make_figure5_k_subpanel(log_y = TRUE)

figure5_05_1_png <- file.path(
  additional_subpanel_dir,
  "05_1_uptake_rate_by_trait_group_and_added_glucose_linear_y.png"
)
figure5_05_1_pdf <- sub("[.]png$", ".pdf", figure5_05_1_png)
figure5_05_2_png <- file.path(
  additional_subpanel_dir,
  "05_2_uptake_rate_by_trait_group_and_added_glucose_log_y.png"
)
figure5_05_2_pdf <- sub("[.]png$", ".pdf", figure5_05_2_png)

ggplot2::ggsave(
  figure5_05_1_png, figure5_05_1, width = 3.2, height = 2.4,
  dpi = 400, bg = "white"
)
ggplot2::ggsave(
  figure5_05_1_pdf, figure5_05_1, width = 3.2, height = 2.4,
  device = grDevices::cairo_pdf
)
ggplot2::ggsave(
  figure5_05_2_png, figure5_05_2, width = 3.2, height = 2.4,
  dpi = 400, bg = "white"
)
ggplot2::ggsave(
  figure5_05_2_pdf, figure5_05_2, width = 3.2, height = 2.4,
  device = grDevices::cairo_pdf
)
utils::write.csv(
  figure5v2_k_statistics,
  file.path(additional_subpanel_dir, "05_1_05_2_uptake_rate_paired_tests.csv"),
  row.names = FALSE
)

figure5_05_1
figure5_05_2
```

## Figure S1

```{r assemble-figure-s1, fig.width=7.1, fig.height=4.6, out.width="100%"}
figure_s1_states <- ggplot2::map_data("state")

figure_s1a <- ggplot2::ggplot() +
  ggplot2::geom_polygon(
    data = figure_s1_states,
    ggplot2::aes(long, lat, group = group),
    fill = "grey96", colour = "grey70", linewidth = 0.25
  ) +
  ggplot2::geom_point(
    data = dplyr::filter(figure_s1_map_data, in_continental_us),
    ggplot2::aes(longitude, latitude, size = n_strains),
    shape = 21, fill = "#80b1d3", colour = "#2E6F95",
    alpha = 0.72, stroke = 0.35
  ) +
  ggplot2::scale_size_area(max_size = 12, breaks = c(10, 25, 50, 75), name = "Strains") +
  ggplot2::coord_quickmap(xlim = c(-130, -65), ylim = c(23.5, 51.5), expand = FALSE) +
  ggplot2::labs(x = NULL, y = NULL) +
  ggplot2::theme_bw(base_size = 9) +
  ggplot2::theme(
    panel.grid = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    legend.position = c(0.5, -0.085),
    legend.direction = "horizontal",
    legend.background = ggplot2::element_rect(
      fill = scales::alpha("white", 0.82), colour = NA
    ),
    legend.key.width = grid::unit(0.35, "cm"),
    plot.margin = ggplot2::margin(4, 2, 20, 2)
  )

figure_s1b <- ggplot2::ggplot(
  figure_s1_composition_data,
  ggplot2::aes(broad_environment, n_strains, fill = gtdb_class)
) +
  ggplot2::geom_col(width = 0.72, colour = "white", linewidth = 0.15) +
  ggplot2::scale_fill_manual(
    values = gtdb_class_colors,
    breaks = names(gtdb_class_colors),
    name = "Genome-derived\nGTDB-Tk class",
    drop = FALSE
  ) +
  ggplot2::scale_x_discrete(drop = FALSE) +
  ggplot2::labs(x = "Broad environment", y = "Number of strains") +
  ggplot2::guides(fill = ggplot2::guide_legend(ncol = 1, byrow = TRUE)) +
  ggplot2::theme_bw(base_size = 9) +
  ggplot2::theme(
    panel.grid.minor = ggplot2::element_blank(),
    panel.grid.major.x = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_text(angle = 35, hjust = 1),
    legend.position = "right",
    legend.title = ggplot2::element_text(size = 8),
    legend.text = ggplot2::element_text(size = 6.5),
    legend.key.height = grid::unit(0.28, "cm"),
    legend.key.width = grid::unit(0.28, "cm"),
    plot.margin = ggplot2::margin(4, 2, 2, 2)
  )

figure_s1b_legend <- cowplot::get_legend(figure_s1b)
figure_s1 <- (
  patchwork::wrap_elements(full = figure_s1a + ggplot2::labs(tag = "A")) |
    patchwork::wrap_elements(
      full = figure_s1b + ggplot2::labs(tag = "B") +
        ggplot2::theme(legend.position = "none")
    ) |
    patchwork::wrap_elements(full = figure_s1b_legend)
) +
  patchwork::plot_layout(widths = c(0.55, 0.25, 0.20)) &
  ggplot2::theme(plot.tag = ggplot2::element_text(face = "bold", size = 11))

figure_s1_png <- file.path(output_dir, "FigureS1.png")
figure_s1_pdf <- file.path(output_dir, "FigureS1.pdf")
ggplot2::ggsave(
  figure_s1_png, figure_s1, width = 7.1, height = 4.6,
  dpi = 400, bg = "white"
)
ggplot2::ggsave(
  figure_s1_pdf, figure_s1, width = 7.1, height = 4.6,
  device = grDevices::cairo_pdf
)
figure_s1
```

## Figure S2

```{r assemble-figure-s2, fig.width=4.5, fig.height=5.1, out.width="70%"}
figure_s2 <- ggplot2::ggplot(
  figure_s2_data,
  ggplot2::aes(mean_auc_B0_M0, mean_auc_B10_M0)
) +
  ggplot2::geom_abline(
    slope = 1, intercept = 0, linetype = "dashed", color = "grey50"
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = auc_B10_M0_lower, ymax = auc_B10_M0_upper),
    width = 0, alpha = 0.2, linewidth = 0.3, color = "#2E6F95"
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = auc_B0_M0_lower, xmax = auc_B0_M0_upper),
    orientation = "y", width = 0, alpha = 0.2, linewidth = 0.3,
    color = "#2E6F95"
  ) +
  ggplot2::geom_point(alpha = 0.45, size = 1.8, color = "#2E6F95") +
  ggplot2::geom_text(
    data = figure_s2_labels, label = "E. coli metE",
    hjust = 1.1, vjust = -0.7, size = 3, show.legend = FALSE
  ) +
  ggplot2::scale_x_log10(limits = c(0.1, NA)) +
  ggplot2::scale_y_log10(limits = c(0.1, NA)) +
  ggplot2::coord_equal() +
  ggplot2::labs(
    x = "-B12 area under OD curve", y = "+B12 area under OD curve"
  ) +
  ggplot2::theme_bw(base_size = 11) +
  ggplot2::theme(
    panel.grid.minor = ggplot2::element_blank()
  )

figure_s2_png <- file.path(output_dir, "FigureS2.png")
figure_s2_pdf <- file.path(output_dir, "FigureS2.pdf")
ggplot2::ggsave(figure_s2_png, figure_s2, width = 4.5, height = 5.1, dpi = 400, bg = "white")
ggplot2::ggsave(figure_s2_pdf, figure_s2, width = 4.5, height = 5.1, device = grDevices::cairo_pdf)
figure_s2
```

## Figure S3

```{r assemble-figure-s3, fig.width=7.1, fig.height=8.66, out.width="100%"}
figure_s3_tips <- figure_s3_data$tips |>
  dplyr::mutate(
    tree_x = figure_s3_data$tree_y_max - figure_s3_data$cladogram_tip_y,
    tree_y = x,
    genus_label = dplyr::if_else(
      is.na(.data$gtdb_genus) | .data$gtdb_genus == "",
      "Unassigned", .data$gtdb_genus
    )
  )
figure_s3_edges <- figure_s3_data$edges |>
  dplyr::rename(
    old_parent_x = parent_x, old_parent_y = parent_y,
    old_child_x = child_x, old_child_y = child_y
  ) |>
  dplyr::transmute(
    parent_x = figure_s3_data$tree_y_max - old_parent_y,
    parent_y = old_parent_x,
    child_x = figure_s3_data$tree_y_max - old_child_y,
    child_y = old_child_x,
    branch_class
  )
figure_s3_width <- diff(range(c(figure_s3_edges$parent_x, figure_s3_edges$child_x)))

figure_s3 <- ggplot2::ggplot() +
  ggplot2::geom_segment(
    data = figure_s3_edges,
    ggplot2::aes(
      x = parent_x, xend = parent_x, y = parent_y, yend = child_y,
      color = branch_class
    ), linewidth = 0.42
  ) +
  ggplot2::geom_text(
    data = figure_s3_tips,
    ggplot2::aes(
      x = tree_x + figure_s3_width * 0.015,
      y = tree_y,
      label = genus_label
    ),
    hjust = 0, size = 1.35, fontface = "italic", color = "grey15"
  ) +
  ggplot2::geom_segment(
    data = figure_s3_edges,
    ggplot2::aes(
      x = parent_x, xend = child_x, y = child_y, yend = child_y,
      color = branch_class
    ), linewidth = 0.42
  ) +
  ggplot2::scale_color_manual(
    values = gtdb_class_colors,
    breaks = names(gtdb_class_colors),
    limits = names(gtdb_class_colors),
    drop = FALSE, na.value = "grey65", name = "GTDB-Tk class",
    guide = ggplot2::guide_legend(
      override.aes = list(linewidth = 0.9, color = unname(gtdb_class_colors))
    )
  ) +
  ggplot2::coord_cartesian(
    xlim = c(
      min(c(figure_s3_edges$parent_x, figure_s3_edges$child_x)),
      max(c(figure_s3_edges$parent_x, figure_s3_edges$child_x)) + figure_s3_width * 0.35
    ),
    ylim = range(figure_s3_tips$tree_y) + c(-1, 1), clip = "off"
  ) +
  ggplot2::theme_void(base_size = 9) +
  ggplot2::theme(
    legend.position = c(0.02, 0.02),
    legend.justification = c(0, 0),
    legend.background = ggplot2::element_rect(fill = "white", color = NA),
    legend.key.height = grid::unit(0.75, "lines"),
    legend.key.width = grid::unit(1.1, "lines")
  )

figure_s3_png <- file.path(output_dir, "FigureS3.png")
figure_s3_pdf <- file.path(output_dir, "FigureS3.pdf")
ggplot2::ggsave(figure_s3_png, figure_s3, width = 7.1, height = 8.66, dpi = 400, bg = "white")
ggplot2::ggsave(figure_s3_pdf, figure_s3, width = 7.1, height = 8.66, device = grDevices::cairo_pdf)
figure_s3
```

## Figure S4

```{r assemble-figure-s4, fig.width=4.0, fig.height=8.66, out.width="65%"}
figure_s4_theme <- ggplot2::theme_bw(base_size = 9) +
  ggplot2::theme(panel.grid.minor = ggplot2::element_blank())

figure_s4a <- ggplot2::ggplot(
  figure_s4_data$A, ggplot2::aes(total_b12_gm, filtrate_b12_gm)
) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      ymin = filtrate_b12_gm / filtrate_b12_gsd,
      ymax = filtrate_b12_gm * filtrate_b12_gsd
    ), alpha = 0.08, linewidth = 0.35
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      xmin = total_b12_gm / total_b12_gsd,
      xmax = total_b12_gm * total_b12_gsd
    ), orientation = "y", alpha = 0.08, linewidth = 0.35
  ) +
  ggplot2::geom_point(color = "black", alpha = 0.7, size = 1.8) +
  ggplot2::geom_smooth(method = "lm", formula = y ~ x, color = "black", fill = "grey70", linewidth = 0.7) +
  ggplot2::annotate("text", x = 300, y = Inf, label = figure_s4_labels[["A"]], vjust = 1.2, size = 2.6) +
  ggplot2::scale_x_log10(limits = c(30, 3000), expand = c(0, 0)) +
  ggplot2::scale_y_log10(limits = c(1.5, 500), expand = c(0, 0)) +
  ggplot2::labs(x = "Total B12 (pM)", y = "Extracellular B12 (pM)") +
  figure_s4_theme

figure_s4b <- ggplot2::ggplot(
  figure_s4_data$B, ggplot2::aes(uptake_b12_mean, filtrate_b12_gm)
) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      ymin = filtrate_b12_gm / filtrate_b12_gsd,
      ymax = filtrate_b12_gm * filtrate_b12_gsd
    ), alpha = 0.08, linewidth = 0.35
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = uptake_b12_mean - uptake_b12_sd, xmax = uptake_b12_mean + uptake_b12_sd),
    orientation = "y", alpha = 0.08, linewidth = 0.35
  ) +
  ggplot2::geom_point(color = "black", alpha = 0.7, size = 1.8) +
  ggplot2::geom_smooth(method = "lm", formula = y ~ x, color = "black", fill = "grey70", linewidth = 0.7) +
  ggplot2::annotate("text", x = 200, y = Inf, label = figure_s4_labels[["B"]], vjust = 1.2, size = 2.6) +
  ggplot2::scale_x_continuous(limits = c(-300, 700), expand = c(0, 0)) +
  ggplot2::scale_y_log10(limits = c(1.5, 500), expand = c(0, 0)) +
  ggplot2::labs(x = "B12 uptake from 500pM", y = "Extracellular B12 (pM)") +
  figure_s4_theme

figure_s4c <- ggplot2::ggplot(
  figure_s4_data$C, ggplot2::aes(uptake_b12_mean, filtrate_proportion_gm)
) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      ymin = filtrate_proportion_gm / filtrate_proportion_gsd,
      ymax = filtrate_proportion_gm * filtrate_proportion_gsd
    ), alpha = 0.08, linewidth = 0.35
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = uptake_b12_mean - uptake_b12_sd, xmax = uptake_b12_mean + uptake_b12_sd),
    orientation = "y", alpha = 0.08, linewidth = 0.35
  ) +
  ggplot2::geom_point(color = "black", alpha = 0.7, size = 1.8) +
  ggplot2::geom_smooth(method = "lm", formula = y ~ x, color = "black", fill = "grey70", linewidth = 0.7) +
  ggplot2::annotate("text", x = 200, y = Inf, label = figure_s4_labels[["C"]], vjust = 1.2, size = 2.6) +
  ggplot2::scale_x_continuous(limits = c(-300, 700), expand = c(0, 0)) +
  ggplot2::scale_y_log10(limits = c(0.001, 2)) +
  ggplot2::labs(x = "B12 uptake from 500pM", y = "Extracellular B12 fraction") +
  figure_s4_theme

figure_s4 <- figure_s4a / figure_s4b / figure_s4c +
  patchwork::plot_layout(heights = c(1, 1, 1)) +
  patchwork::plot_annotation(tag_levels = "A") &
  ggplot2::theme(plot.tag = ggplot2::element_text(face = "bold", size = 11))

figure_s4_png <- file.path(output_dir, "FigureS4.png")
figure_s4_pdf <- file.path(output_dir, "FigureS4.pdf")
ggplot2::ggsave(figure_s4_png, figure_s4, width = 4.0, height = 8.66, dpi = 400, bg = "white")
ggplot2::ggsave(figure_s4_pdf, figure_s4, width = 4.0, height = 8.66, device = grDevices::cairo_pdf)
figure_s4
```

## Figure S5

```{r assemble-figure-s5, fig.width=7.1, fig.height=8.06, out.width="100%"}
figure_s5_theme <- ggplot2::theme_bw(base_size = 10) +
  ggplot2::theme(panel.grid.minor = ggplot2::element_blank())

permutation_chisq_cramers_v <- function(data, trait_group, seed, B = 9999L) {
  data <- data |>
    dplyr::filter(gtdb_class != "Unassigned")
  contingency_table <- table(
    GTDB_class = data$gtdb_class,
    trait_group = data[[trait_group]]
  )
  contingency_table <- contingency_table[
    rowSums(contingency_table) > 0,
    colSums(contingency_table) > 0,
    drop = FALSE
  ]
  set.seed(seed)
  test <- stats::chisq.test(
    contingency_table,
    simulate.p.value = TRUE,
    B = B
  )
  cramers_v <- sqrt(
    unname(test$statistic) /
      (sum(contingency_table) * min(nrow(contingency_table) - 1, ncol(contingency_table) - 1))
  )
  list(table = contingency_table, test = test, cramers_v = cramers_v)
}

format_figure_s5_test <- function(result) {
  p_text <- if (result$test$p.value < 0.001) {
    "p < 0.001"
  } else {
    paste0("p = ", formatC(result$test$p.value, format = "f", digits = 3))
  }
  paste0(
    "Permutation chi-square test\n",
    p_text, ", Cramer's V = ",
    formatC(result$cramers_v, format = "f", digits = 3)
  )
}

figure_s5_data$A <- figure_s5_data$A |>
  dplyr::mutate(
    figure_s5_trait_group = dplyr::recode(
      b12_trait_group1,
      bystander = "Bystander",
      scavenger = "Scavenger",
      reclaimer = "Reclaimer",
      sharer = "Non-Reclaimer"
    )
  )
figure_s5_data$B <- figure_s5_data$B |>
  dplyr::mutate(
    figure_s5_trait_group = dplyr::recode(
      b12_trait_group2,
      retainer = "Retainer",
      provider = "Provider",
      reclaimer = "Reclaimer"
    )
  )

figure_s5a_test <- permutation_chisq_cramers_v(
  figure_s5_data$A, "figure_s5_trait_group", seed = 20260825L
)
figure_s5b_test <- permutation_chisq_cramers_v(
  figure_s5_data$B, "figure_s5_trait_group", seed = 20260826L
)
figure_s5a_test_label <- format_figure_s5_test(figure_s5a_test)
figure_s5b_test_label <- format_figure_s5_test(figure_s5b_test)

figure_s5a_labels <- data.frame(
  text = c("Bystander", "Scavenger", "Reclaimer", "Non-Reclaimer"),
  x = c(5, 5, 400, 400), y = c(-200, 700, 700, -200)
)
figure_s5a <- ggplot2::ggplot(
  figure_s5_data$A, ggplot2::aes(total_b12_gm_plot, uptake_b12_mean)
) +
  density_layer_figure1() +
  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = uptake_b12_mean - uptake_b12_sd, ymax = uptake_b12_mean + uptake_b12_sd),
    alpha = 0.08, linewidth = 0.35
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = total_b12_gm / total_b12_gsd, xmax = total_b12_gm * total_b12_gsd),
    orientation = "y", alpha = 0.08, linewidth = 0.35
  ) +
  ggplot2::geom_point(ggplot2::aes(color = gtdb_class), alpha = 0.78, size = 2.1) +
  ggplot2::scale_color_manual(
    values = gtdb_class_colors, breaks = names(gtdb_class_colors),
    name = paste0(figure_s5a_test_label, "\n\nGTDB-Tk class")
  ) +
  ggplot2::scale_x_log10(limits = c(1, 2000), expand = c(0, 0)) +
  ggplot2::scale_y_continuous(breaks = c(-250, 0, 250, 500, 750), limits = c(-250, 750), expand = c(0, 0)) +
  ggplot2::coord_cartesian(ylim = c(-250, 750), expand = FALSE) +
  ggplot2::geom_hline(yintercept = 250, linetype = "dashed", colour = "grey40") +
  ggplot2::geom_vline(xintercept = 50, linetype = "dashed", colour = "grey40") +
  ggplot2::geom_text(
    data = figure_s5a_labels, ggplot2::aes(x = x, y = y, label = text),
    inherit.aes = FALSE, size = 3.4
  ) +
  ggplot2::labs(x = "Total B12 synthesis (pM)", y = "B12 uptake from 500 pM addition") +
  ggplot2::guides(fill = "none") + figure_s5_theme

figure_s5b_labels <- data.frame(
  text = c("Retainer", "Provider", "Reclaimer"),
  x = c(0.005, 0.8, 0.05), y = c(-200, -200, 700)
)
figure_s5b <- ggplot2::ggplot(
  figure_s5_data$B, ggplot2::aes(filtrate_proportion_gm, uptake_b12_mean)
) +
  density_layer_figure1() +
  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = uptake_b12_mean - uptake_b12_sd, ymax = uptake_b12_mean + uptake_b12_sd),
    alpha = 0.08, linewidth = 0.35
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      xmin = filtrate_proportion_gm / filtrate_proportion_gsd,
      xmax = filtrate_proportion_gm * filtrate_proportion_gsd
    ), orientation = "y", alpha = 0.08, linewidth = 0.35
  ) +
  ggplot2::geom_point(ggplot2::aes(color = gtdb_class), alpha = 0.78, size = 2.1) +
  ggplot2::scale_color_manual(
    values = gtdb_class_colors, breaks = names(gtdb_class_colors),
    name = paste0(figure_s5b_test_label, "\n\nGTDB-Tk class")
  ) +
  ggplot2::scale_x_log10(limits = c(0.001, 2), expand = c(0, 0)) +
  ggplot2::scale_y_continuous(breaks = c(-250, 0, 250, 500, 750), limits = c(-250, 750), expand = c(0, 0)) +
  ggplot2::coord_cartesian(ylim = c(-250, 750), expand = FALSE) +
  ggplot2::geom_hline(yintercept = 250, linetype = "dashed", colour = "grey40") +
  ggplot2::geom_segment(
    data = data.frame(x = 0.05, xend = 0.05, y = -250, yend = 250),
    ggplot2::aes(x = x, xend = xend, y = y, yend = yend), inherit.aes = FALSE,
    linetype = "dashed", colour = "grey40"
  ) +
  ggplot2::geom_text(
    data = figure_s5b_labels, ggplot2::aes(x = x, y = y, label = text),
    inherit.aes = FALSE, size = 3.4
  ) +
  ggplot2::labs(x = "Extracellular B12 fraction", y = "B12 uptake from 500 pM addition") +
  ggplot2::guides(fill = "none") + figure_s5_theme

figure_s5 <- figure_s5a / figure_s5b +
  patchwork::plot_layout(heights = c(1, 1), guides = "keep") +
  patchwork::plot_annotation(tag_levels = "A") &
  ggplot2::theme(plot.tag = ggplot2::element_text(face = "bold", size = 11))

figure_s5_png <- file.path(output_dir, "FigureS5.png")
figure_s5_pdf <- file.path(output_dir, "FigureS5.pdf")
ggplot2::ggsave(figure_s5_png, figure_s5, width = 7.1, height = 8.06, dpi = 400, bg = "white")
ggplot2::ggsave(figure_s5_pdf, figure_s5, width = 7.1, height = 8.06, device = grDevices::cairo_pdf)
figure_s5
```

## Figure S6

```{r assemble-figure-s6, fig.width=7.1, fig.height=8.66, out.width="100%"}
make_binary_tree_panel <- function(tip_data, panel_title) {
  panel_tree <- ape::keep.tip(tree, intersect(tree$tip.label, tip_data$tip_label))
  graphics::plot(panel_tree, direction = "downwards", show.tip.label = FALSE, plot = FALSE)
  layout <- get("last_plot.phylo", envir = ape::.PlotPhyloEnv)
  edges <- data.frame(
    parent = panel_tree$edge[, 1], child = panel_tree$edge[, 2],
    x = layout$xx[panel_tree$edge[, 1]], y = layout$yy[panel_tree$edge[, 1]],
    xend = layout$xx[panel_tree$edge[, 2]], yend = layout$yy[panel_tree$edge[, 2]]
  )
  tree_y_max <- max(layout$yy, na.rm = TRUE)
  tips <- data.frame(
    tip_label = panel_tree$tip.label,
    tree_x = tree_y_max - layout$yy[seq_along(panel_tree$tip.label)],
    tree_y = layout$xx[seq_along(panel_tree$tip.label)]
  ) |>
    dplyr::left_join(tip_data, by = "tip_label")
  edge_orders <- stats::setNames(tips$order_taxonomy, seq_len(nrow(tips)))
  descendants <- get_descendant_tips_figure1(panel_tree)
  edges$order_taxonomy <- vapply(edges$child, function(node) {
    vals <- unique(na.omit(edge_orders[as.character(descendants(node))]))
    if (length(vals) == 1) vals else "Mixed"
  }, character(1))
  edges <- edges |>
    dplyr::transmute(
      parent_x = tree_y_max - y, parent_y = x,
      child_x = tree_y_max - yend, child_y = xend,
      order_taxonomy
    )
  tree_width <- diff(range(c(edges$parent_x, edges$child_x), na.rm = TRUE))
  tile_width <- tree_width * 0.045
  tile_gap <- tile_width * 0.35
  tile_positions <- max(tips$tree_x) + tile_gap + tile_width * c(0.5, 1.85, 3.2)
  tip_extensions <- tips |>
    dplyr::transmute(
      x = tree_x, xend = tile_positions[1] - tile_width / 2,
      y = tree_y, yend = tree_y, order_taxonomy
    )
  trait_names <- c("total_b12_binary", "uptake_b12_binary", "filtrate_proportion_binary")
  trait_labels <- c("B12 synthesis", "B12 uptake", "EC-B12 fraction")
  tile_data <- tips |>
    dplyr::select(tree_y, dplyr::all_of(trait_names)) |>
    tidyr::pivot_longer(-tree_y, names_to = "trait", values_to = "value") |>
    dplyr::mutate(
      trait = factor(trait, levels = trait_names, labels = trait_labels),
      tile_x = tile_positions[as.numeric(trait)],
      fill_key = paste(as.character(trait), as.character(value), sep = ": ")
    )
  header_data <- data.frame(
    x = tile_positions, y = max(tips$tree_y) + 4,
    label = trait_labels
  )
  ggplot2::ggplot() +
    ggplot2::geom_segment(data = edges, ggplot2::aes(x = parent_x, xend = parent_x, y = parent_y, yend = child_y, color = order_taxonomy), linewidth = 0.35) +
    ggplot2::geom_segment(data = edges, ggplot2::aes(x = parent_x, xend = child_x, y = child_y, yend = child_y, color = order_taxonomy), linewidth = 0.35) +
    ggplot2::geom_segment(data = tip_extensions, ggplot2::aes(x = x, xend = xend, y = y, yend = yend, color = order_taxonomy), linewidth = 0.35) +
    ggplot2::geom_tile(data = dplyr::filter(tile_data, trait == "B12 synthesis"), ggplot2::aes(x = tile_x, y = tree_y, fill = value), width = tile_width, height = 0.92) +
    ggplot2::scale_fill_manual(values = c(Below = "grey88", Above = "#2166ac"), limits = c("Below", "Above"), name = "B12 synthesis", drop = FALSE, guide = ggplot2::guide_legend(ncol = 1, order = 2)) +
    ggnewscale::new_scale_fill() +
    ggplot2::geom_tile(data = dplyr::filter(tile_data, trait == "B12 uptake"), ggplot2::aes(x = tile_x, y = tree_y, fill = value), width = tile_width, height = 0.92) +
    ggplot2::scale_fill_manual(values = c(Below = "grey88", Above = "#b2182b"), limits = c("Below", "Above"), name = "B12 uptake", drop = FALSE, guide = ggplot2::guide_legend(ncol = 1, order = 3)) +
    ggnewscale::new_scale_fill() +
    ggplot2::geom_tile(data = dplyr::filter(tile_data, trait == "EC-B12 fraction"), ggplot2::aes(x = tile_x, y = tree_y, fill = value), width = tile_width, height = 0.92) +
    ggplot2::scale_fill_manual(values = c(Below = "grey88", Above = "#d95f02"), limits = c("Below", "Above"), name = "EC-B12 fraction", drop = FALSE, guide = ggplot2::guide_legend(ncol = 1, order = 4)) +
    ggplot2::geom_text(data = header_data, ggplot2::aes(x = x, y = y, label = label), inherit.aes = FALSE, angle = 45, hjust = 0, size = 2.4) +
    ggplot2::scale_color_manual(values = gtdb_order_colors, breaks = names(gtdb_order_colors), limits = names(gtdb_order_colors), name = "GTDB-Tk order", drop = FALSE, guide = ggplot2::guide_legend(ncol = 1, order = 1)) +
    ggplot2::coord_cartesian(
      xlim = c(min(edges$parent_x), max(tile_positions) + tile_width),
      ylim = c(min(tips$tree_y) - 1, max(tips$tree_y) + 13), clip = "off"
    ) +
    ggplot2::labs(title = panel_title) +
    ggplot2::theme_void(base_size = 7) +
    ggplot2::theme(
      plot.title = ggplot2::element_text(size = 10),
      legend.position = "top", legend.box = "horizontal",
      legend.direction = "vertical",
      legend.title = ggplot2::element_text(face = "bold", size = 7),
      legend.text = ggplot2::element_text(size = 6),
      legend.key.width = grid::unit(1.1, "lines"),
      legend.key.height = grid::unit(0.75, "lines"),
      legend.spacing.x = grid::unit(1.2, "lines"),
      legend.margin = ggplot2::margin(0, 0, 0, 0)
    )
}
figure_s6a <- make_binary_tree_panel(figure_s6_data$A, "All strains")
figure_s6b <- make_binary_tree_panel(figure_s6_data$B, expression(B[12]~synthesizers))
figure_s6_legend <- cowplot::get_legend(
  figure_s6a + ggplot2::theme(legend.position = "right", legend.box = "vertical", legend.direction = "vertical")
)
figure_s6_body <- (
  (figure_s6a + ggplot2::labs(tag = "A") + ggplot2::theme(legend.position = "none")) |
    (figure_s6b + ggplot2::labs(tag = "B") + ggplot2::theme(legend.position = "none"))
) & ggplot2::theme(plot.tag = ggplot2::element_text(face = "bold", size = 11))
figure_s6 <- (patchwork::wrap_elements(full = figure_s6_body) | patchwork::wrap_elements(full = figure_s6_legend)) +
  patchwork::plot_layout(widths = c(0.78, 0.22))
figure_s6_png <- file.path(output_dir, "FigureS6.png"); figure_s6_pdf <- file.path(output_dir, "FigureS6.pdf")
ggplot2::ggsave(figure_s6_png, figure_s6, width = 7.1, height = 8.66, dpi = 400, bg = "white")
ggplot2::ggsave(figure_s6_pdf, figure_s6, width = 7.1, height = 8.66, device = grDevices::cairo_pdf)
figure_s6
```

## Figure S7

```{r assemble-figure-s7, fig.width=7.1, fig.height=4.28, out.width="100%"}
figure_s7 <- ggplot2::ggplot(figure_s7_data, ggplot2::aes(mean_permutation_importance, reorder(ko_gene_label, mean_permutation_importance))) +
  ggplot2::geom_col(fill = "#4E79A7", width = 0.72) +
  ggplot2::geom_errorbar(ggplot2::aes(xmin = pmax(0, mean_permutation_importance - sd_permutation_importance), xmax = mean_permutation_importance + sd_permutation_importance), orientation = "y", width = 0.2, linewidth = 0.35) +
  ggplot2::facet_wrap(
    ggplot2::vars(facet_label),
    ncol = 4, scales = "free_y", labeller = ggplot2::label_value
  ) +
  ggplot2::labs(x = "Mean permutation feature importance ± SD", y = NULL) +
  ggplot2::theme_bw(base_size = 7) +
  ggplot2::theme(panel.grid.minor = ggplot2::element_blank(), strip.text = ggplot2::element_text(face = "bold", size = 7))
figure_s7_png <- file.path(output_dir, "FigureS7.png"); figure_s7_pdf <- file.path(output_dir, "FigureS7.pdf")
ggplot2::ggsave(figure_s7_png, figure_s7, width = 7.1, height = 4.28, dpi = 400, bg = "white")
ggplot2::ggsave(figure_s7_pdf, figure_s7, width = 7.1, height = 4.28, device = grDevices::cairo_pdf)
figure_s7
```

## Figure S8

```{r assemble-figure-s8, fig.width=7.1, fig.height=3.28, out.width="100%"}
figure_s8_stats <- figure_s8_data |>
  dplyr::group_by(phenotype) |>
  dplyr::summarise(
    pearson_r = stats::cor(
      mean_permutation_importance,
      pyseer_neg_log10_BH_adjusted_lrt_pvalue,
      use = "complete.obs", method = "pearson"
    ),
    .groups = "drop"
  )
figure_s8 <- ggplot2::ggplot(figure_s8_data, ggplot2::aes(mean_permutation_importance, pyseer_neg_log10_BH_adjusted_lrt_pvalue, color = feature_group)) +
  ggplot2::geom_hline(yintercept = -log10(0.05), linetype = "dashed", color = "grey40") +
  ggplot2::geom_point(alpha = 0.65, size = 1.2) +
  ggrepel::geom_text_repel(
    data = dplyr::filter(figure_s8_data, !is.na(gene_name), mean_permutation_importance > 0.004, pyseer_neg_log10_BH_adjusted_lrt_pvalue > 4.5),
    ggplot2::aes(label = gene_name), size = 2.4, show.legend = FALSE,
    seed = 20260820, box.padding = 0.3, point.padding = 0.15,
    min.segment.length = 0, max.overlaps = Inf
  ) +
  ggplot2::geom_text(data = figure_s8_stats, ggplot2::aes(x = -Inf, y = Inf, label = sprintf("Pearson's r = %.3f", pearson_r)), inherit.aes = FALSE, hjust = -0.1, vjust = 1.2, size = 3) +
  ggplot2::scale_color_manual(values = c(
    "B12 transporter" = "#F8766D",
    "Corrin ring" = "#A3A500",
    "Late/salvage" = "#00BF7D",
    "Not B12 transporter" = "grey60",
    "Not in KEGG\nB12 module" = "grey60"
  )) +
  ggplot2::facet_wrap(~phenotype, nrow = 1, scales = "free_x") +
  ggplot2::labs(x = "Mean permutation RF feature importance", y = expression("Pyseer "*-log[10]*"(BH-adj p-val)"), color = "Feature group") +
  ggplot2::theme_bw(base_size = 9) + ggplot2::theme(panel.grid.minor = ggplot2::element_blank(), strip.text = ggplot2::element_text(face = "bold"), legend.position = "right")
figure_s8_png <- file.path(output_dir, "FigureS8.png"); figure_s8_pdf <- file.path(output_dir, "FigureS8.pdf")
ggplot2::ggsave(figure_s8_png, figure_s8, width = 7.1, height = 3.28, dpi = 400, bg = "white")
ggplot2::ggsave(figure_s8_pdf, figure_s8, width = 7.1, height = 3.28, device = grDevices::cairo_pdf)
figure_s8
```

## Figures S9-S13

```{r assemble-figures-s9-s13, fig.width=7.1, fig.height=3.7, out.width="100%"}
facet_theme <- ggplot2::theme_bw(base_size = 7) + ggplot2::theme(panel.grid.minor = ggplot2::element_blank(), strip.text = ggplot2::element_text(size = 6), legend.position = "none")
facet_scale <- ggplot2::scale_color_manual(values = c(blank = "grey55", `NA` = "grey55", trait_group_colors), drop = FALSE)

figure_s9 <- ggplot2::ggplot(figure_s9_data, ggplot2::aes(killed_proportion_source_od600, adjusted_live_stain, color = trait_group2, group = interaction(experiment_name, biological_replicate))) +
  ggplot2::geom_line(linewidth = 0.45) + ggplot2::geom_point(size = 0.8) + facet_scale +
  ggplot2::facet_wrap(ggplot2::vars(trait_group2_strain_label), ncol = 8, drop = FALSE) +
  ggplot2::labs(x = "Killed proportion × source-culture OD600 at 0 min", y = "Dead cell stain (DCS1) fluorescence") + facet_theme

figure_s10_data <- figure_s10_data |>
  dplyr::mutate(
    b12_trait_group2 = factor(b12_trait_group2, levels = trait_group_levels)
  )
figure_s10_tests <- figure_s10_data |>
  dplyr::group_by(b12_trait_group2) |>
  dplyr::group_modify(function(.x, .y) {
    test <- stats::t.test(
      log10(.x$extracellular_b12_over_dead_fraction), mu = 0
    )
    tibble::tibble(
      p_value = test$p.value,
      annotation_y = max(.x$extracellular_b12_over_dead_fraction) * 1.35
    )
  }) |>
  dplyr::ungroup() |>
  dplyr::mutate(
    p_label = dplyr::if_else(
      p_value < 0.001, "p < 0.001",
      paste0("p = ", formatC(p_value, format = "f", digits = 3))
    )
  )
figure_s10 <- ggplot2::ggplot(
  figure_s10_data,
  ggplot2::aes(
    b12_trait_group2, extracellular_b12_over_dead_fraction,
    color = b12_trait_group2
  )
) +
  ggplot2::geom_hline(
    yintercept = 1, linetype = "dashed", color = "grey40", linewidth = 0.6
  ) +
  ggplot2::geom_boxplot(outlier.shape = NA, linewidth = 0.5, alpha = 0.25) +
  ggplot2::geom_point(
    position = ggplot2::position_jitter(width = 0.1, height = 0, seed = 20260820),
    alpha = 0.78, size = 2.2
  ) +
  ggplot2::geom_text(
    data = figure_s10_tests,
    ggplot2::aes(x = b12_trait_group2, y = annotation_y, label = p_label),
    inherit.aes = FALSE, size = 3.4, vjust = 0
  ) +
  ggplot2::scale_color_manual(
    values = trait_group_colors, breaks = trait_group_levels, drop = FALSE
  ) +
  ggplot2::scale_y_log10(
    expand = ggplot2::expansion(mult = c(0.05, 0.18))
  ) +
  ggplot2::labs(
    x = "Trait group",
    y = expression(frac("Extracellular B12 fraction", "Dead cell fraction"))
  ) +
  ggplot2::theme_bw(base_size = 11) +
  ggplot2::theme(legend.position = "none", panel.grid.minor = ggplot2::element_blank())

figure_s11 <- ggplot2::ggplot(figure_s11_data, ggplot2::aes(sample_time_minute / 60, color = trait_group2, group = strain_id)) +
  ggplot2::geom_hline(yintercept = 500, linetype = "dashed", color = "grey50") +
  ggplot2::geom_line(ggplot2::aes(y = model_pred), linewidth = 0.55) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin = b12_ymin, ymax = b12_ymax), width = 0, alpha = 0.3, linewidth = 0.25) +
  ggplot2::geom_point(ggplot2::aes(y = empirical_mean_b12), size = 0.9) + facet_scale +
  ggplot2::facet_wrap(ggplot2::vars(trait_group2_strain_label), ncol = 8, drop = FALSE) +
  ggplot2::labs(x = "Time (hours)", y = "Extracellular B12 (pM)") + facet_theme

figure_s12 <- ggplot2::ggplot(figure_s12_data, ggplot2::aes(killed_proportion, color = trait_group2, group = strain_id)) +
  ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "grey65") +
  ggplot2::geom_line(ggplot2::aes(y = predicted_b12_frac), linewidth = 0.55) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin = b12_frac_ymin, ymax = b12_frac_ymax), width = 0.015, alpha = 0.25, linewidth = 0.25) +
  ggplot2::geom_point(ggplot2::aes(y = b12_frac_mean), size = 0.9) + facet_scale +
  ggplot2::scale_x_continuous(breaks = c(0, 0.5, 1)) +
  ggplot2::scale_y_continuous(limits = c(NA, 1.5)) + ggplot2::facet_wrap(ggplot2::vars(trait_group2_strain_label), ncol = 8, drop = FALSE) +
  ggplot2::labs(x = "Fraction killed: f", y = "Extracellular B12 fraction: B(1,f)/b") + facet_theme

figure_s13 <- ggplot2::ggplot(figure_s13_model, ggplot2::aes(sample_time_minute / 60, color = trait_group2, group = interaction(strain_id, added_glucose_mM_C_factor))) +
  ggplot2::geom_line(ggplot2::aes(y = model_pred, linetype = added_glucose_mM_C_factor), linewidth = 0.55) +
  ggplot2::geom_errorbar(data = figure_s13_empirical, ggplot2::aes(ymin = mean_b12 - sd_b12, ymax = mean_b12 + sd_b12), width = 0, alpha = 0.25, linewidth = 0.25) +
  ggplot2::geom_point(data = figure_s13_empirical, ggplot2::aes(y = mean_b12, shape = added_glucose_mM_C_factor), size = 1) +
  facet_scale + ggplot2::scale_shape_manual(values = c(`0` = 16, `10` = 17), name = "Glucose (mM C)") +
  ggplot2::scale_linetype_manual(values = c(`0` = "solid", `10` = "dashed"), name = "Glucose (mM C)") +
  ggplot2::facet_wrap(ggplot2::vars(trait_group2_strain_label), ncol = 8, drop = FALSE) +
  ggplot2::labs(x = "Time (hours)", y = "Extracellular B12 (pM)") + facet_theme +
  ggplot2::theme(legend.position = "right") + ggplot2::guides(color = "none")

supp_plots <- list(S9 = figure_s9, S10 = figure_s10, S11 = figure_s11, S12 = figure_s12, S13 = figure_s13)
supp_widths <- c(S9 = 7.1, S10 = 3.64, S11 = 7.1, S12 = 7.1, S13 = 7.1)
supp_heights <- c(S9 = 3.76, S10 = 4.2, S11 = 3.73, S12 = 3.73, S13 = 3.33)
for (nm in names(supp_plots)) {
  png_path <- file.path(output_dir, paste0("Figure", nm, ".png")); pdf_path <- file.path(output_dir, paste0("Figure", nm, ".pdf"))
  ggplot2::ggsave(png_path, supp_plots[[nm]], width = supp_widths[[nm]], height = supp_heights[[nm]], dpi = 400, bg = "white")
  ggplot2::ggsave(pdf_path, supp_plots[[nm]], width = supp_widths[[nm]], height = supp_heights[[nm]], device = grDevices::cairo_pdf)
  assign(paste0("figure_", tolower(nm), "_png"), png_path)
  assign(paste0("figure_", tolower(nm), "_pdf"), pdf_path)
}
figure_s13
```

## Figure S14

```{r assemble-figure-s14, fig.width=7.1, fig.height=5.28, out.width="100%"}
figure_s14_theme <- ggplot2::theme_bw(base_size = 8) +
  ggplot2::theme(
    plot.title = ggplot2::element_text(
      size = 8, face = "bold", hjust = 0.5,
      margin = ggplot2::margin(b = 3)
    ),
    plot.subtitle = ggplot2::element_blank(),
    legend.position = "none",
    panel.grid.minor = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_text(angle = 0, hjust = 0.5),
    strip.text = ggplot2::element_text(size = 6.5),
    plot.margin = ggplot2::margin(3, 3, 3, 3)
  )

make_figure_s14_paired_plot <- function(
  dat, statistics, value_column, y_label, panel_title,
  log_y = FALSE, reference_y = NULL
) {
  value_column <- rlang::ensym(value_column)
  p <- ggplot2::ggplot(
    dat,
    ggplot2::aes(x = added_glucose_mM_C, y = !!value_column)
  ) +
    ggplot2::geom_boxplot(
      width = 0.55, outlier.shape = NA,
      fill = "grey88", color = "grey30", linewidth = 0.4
    ) +
    ggplot2::geom_line(
      ggplot2::aes(group = strain_id),
      color = "grey45", linewidth = 0.3, alpha = 0.28
    ) +
    ggplot2::geom_point(
      ggplot2::aes(color = b12_trait_group2),
      position = ggplot2::position_jitter(
        width = 0.08, height = 0, seed = 20260821
      ),
      size = 1.15, alpha = 0.82
    ) +
    ggplot2::geom_segment(
      data = statistics,
      ggplot2::aes(x = 1, xend = 2, y = segment_y, yend = segment_y),
      inherit.aes = FALSE, linewidth = 0.35, color = "black"
    ) +
    ggplot2::geom_text(
      data = statistics,
      ggplot2::aes(x = 1.5, y = label_y, label = p_label),
      inherit.aes = FALSE, size = 2.15, vjust = 0, color = "black"
    ) +
    ggplot2::scale_color_manual(
      values = trait_group_colors, breaks = trait_group_levels
    ) +
    ggplot2::facet_wrap(ggplot2::vars(b12_trait_group2), nrow = 1) +
    ggplot2::labs(
      x = "Added glucose (mM C)", y = y_label,
      title = panel_title, subtitle = NULL, color = NULL
    ) +
    figure_s14_theme

  if (!is.null(reference_y)) {
    p <- p + ggplot2::geom_hline(
      yintercept = reference_y, linetype = "dashed",
      color = "grey55", linewidth = 0.35
    )
  }
  if (log_y) {
    p + ggplot2::scale_y_log10(limits = c(NA, unique(statistics$upper_y)))
  } else {
    p + ggplot2::scale_y_continuous(limits = c(0, unique(statistics$upper_y)))
  }
}

figure_s14a <- make_figure_s14_paired_plot(
  figure_s14_data$A, figure_s14_statistics$A, mean_b12,
  "Extracellular B12 (pM)", "No B12 added"
)
figure_s14b <- make_figure_s14_paired_plot(
  figure_s14_data$B, figure_s14_statistics$B, mean_b12,
  "Extracellular B12 (pM)", "500pM B12 added", reference_y = 500
)
figure_s14c <- make_figure_s14_paired_plot(
  figure_s14_data$C, figure_s14_statistics$C, mean_measurement,
  "Adjusted OD600", "No B12 added"
)
figure_s14d <- make_figure_s14_paired_plot(
  figure_s14_data$D, figure_s14_statistics$D, mean_measurement,
  "Dead cell fluorescence", "No B12 added", log_y = TRUE
)

figure_s14e <- ggplot2::ggplot(
  figure_s14_data$E,
  ggplot2::aes(
    x = mean_filtrate_b12_per_adjusted_live_stain_glucose_0,
    y = mean_filtrate_b12_per_adjusted_live_stain_glucose_10,
    color = b12_trait_group2
  )
) +
  ggplot2::geom_abline(
    slope = 1, intercept = 0, linetype = "dashed",
    color = "grey45", linewidth = 0.35
  ) +
  ggplot2::geom_point(size = 1.45, alpha = 0.82) +
  ggplot2::scale_x_log10() +
  ggplot2::scale_y_log10() +
  ggplot2::scale_color_manual(
    values = trait_group_colors, breaks = trait_group_levels
  ) +
  ggplot2::labs(
    x = "EC-B12/Dead cell signal\n when glucose = 0mM C",
    y = "EC-B12/Dead cell signal\n when glucose = 10mM C",
    title = "No B12 added", subtitle = NULL, color = NULL
  ) +
  figure_s14_theme

figure_s14f <- ggplot2::ggplot(
  figure_s14_data$F,
  ggplot2::aes(
    x = b12_trait_group2, y = glucose_10_over_0,
    color = b12_trait_group2, fill = b12_trait_group2
  )
) +
  ggplot2::geom_hline(
    yintercept = 1, linetype = "dashed",
    color = "grey55", linewidth = 0.35
  ) +
  ggplot2::geom_boxplot(
    width = 0.55, outlier.shape = NA, alpha = 0.18, linewidth = 0.4
  ) +
  ggplot2::geom_jitter(
    width = 0.08, height = 0, size = 1.15, alpha = 0.82
  ) +
  ggplot2::geom_text(
    data = figure_s14f_tests,
    ggplot2::aes(
      x = b12_trait_group2, y = annotation_y, label = p_label
    ),
    inherit.aes = FALSE, size = 2.15, vjust = 0, color = "black"
  ) +
  ggplot2::scale_color_manual(
    values = trait_group_colors, breaks = trait_group_levels
  ) +
  ggplot2::scale_fill_manual(
    values = trait_group_colors, breaks = trait_group_levels
  ) +
  ggplot2::scale_y_log10(
    expand = ggplot2::expansion(mult = c(0.05, 0.18))
  ) +
  ggplot2::labs(
    x = "Trait group",
    y = "EC-B12/Dead cell signal\n when Glucose = 10mM/0mM",
    title = "No B12 added", subtitle = NULL, color = NULL, fill = NULL
  ) +
  figure_s14_theme

figure_s14 <- patchwork::wrap_plots(
  A = figure_s14a, B = figure_s14b, C = figure_s14c,
  D = figure_s14d, E = figure_s14e, F = figure_s14f,
  design = "ABC\nDEF"
) +
  patchwork::plot_annotation(tag_levels = "A") &
  ggplot2::theme(
    plot.tag = ggplot2::element_text(face = "bold", size = 11),
    plot.tag.position = c(0, 1)
  )

figure_s14_png <- file.path(output_dir, "FigureS14.png")
figure_s14_pdf <- file.path(output_dir, "FigureS14.pdf")
ggplot2::ggsave(
  figure_s14_png, figure_s14, width = 7.1, height = 5.28,
  dpi = 400, bg = "white"
)
ggplot2::ggsave(
  figure_s14_pdf, figure_s14, width = 7.1, height = 5.28,
  device = grDevices::cairo_pdf
)
utils::write.csv(
  dplyr::bind_rows(figure_s14_statistics, .id = "panel"),
  file.path(output_dir, "FigureS14_paired_wilcoxon_statistics.csv"),
  row.names = FALSE
)
figure_s14
```

## Figure S15

```{r assemble-figure-s15, fig.width=5.2, fig.height=3.6, out.width="85%"}
figure_s15_fill_limit <- max(
  abs(figure_s15_data$signed_minus_log10_bh_p), na.rm = TRUE
)
if (!is.finite(figure_s15_fill_limit) || figure_s15_fill_limit == 0) {
  figure_s15_fill_limit <- 1
}

figure_s15 <- ggplot2::ggplot(
  figure_s15_data,
  ggplot2::aes(
    x = method,
    y = display_label,
    fill = signed_minus_log10_bh_p
  )
) +
  ggplot2::geom_tile(color = "white", linewidth = 0.4) +
  ggplot2::geom_text(
    ggplot2::aes(label = p_value_label),
    color = "grey15", size = 3
  ) +
  ggplot2::scale_fill_gradient2(
    low = "#B2182B", mid = "white", high = "#2166AC",
    midpoint = 0,
    limits = c(-figure_s15_fill_limit, figure_s15_fill_limit),
    na.value = "grey88"
  ) +
  ggplot2::labs(
    x = NULL,
    y = NULL,
    fill = "Signed\n-log10\nBH p-value"
  ) +
  ggplot2::theme_bw(base_size = 9) +
  ggplot2::theme(
    panel.grid = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_text(size = 8),
    axis.text.y = ggplot2::element_text(size = 8),
    axis.ticks = ggplot2::element_blank(),
    legend.position = "right",
    plot.margin = ggplot2::margin(4, 4, 4, 4)
  )

figure_s15_png <- file.path(output_dir, "FigureS15.png")
figure_s15_pdf <- file.path(output_dir, "FigureS15.pdf")
ggplot2::ggsave(
  figure_s15_png, figure_s15, width = 5.2, height = 3.6,
  dpi = 400, bg = "white"
)
ggplot2::ggsave(
  figure_s15_pdf, figure_s15, width = 5.2, height = 3.6,
  device = grDevices::cairo_pdf
)
figure_s15
```

## Figure S16

```{r assemble-figure-s16, fig.width=7.1, fig.height=5.12, out.width="100%"}
figure_s16_colors <- c(
  blank = "grey35",
  HTWP4 = "#0072B2",
  JW50603 = "#D55E00",
  OTU4908 = "#009E73"
)

figure_s16a <- figure_s16_data |>
  dplyr::filter(
    .data$assay_type == "E. coli OD600",
    .data$assay_plate_number == 1,
    is.finite(.data$od600), .data$od600 > 0
  ) |>
  ggplot2::ggplot(
    ggplot2::aes(
      x = b12_conc_pM, y = od600,
      color = bacteria_strain_id
    )
  ) +
  ggplot2::geom_point(size = 1.05, alpha = 0.62) +
  ggplot2::geom_smooth(se = FALSE, linewidth = 0.65) +
  ggplot2::scale_x_log10(
    breaks = scales::breaks_log(n = 5),
    labels = scales::label_log()
  ) +
  ggplot2::scale_y_log10() +
  ggplot2::scale_color_manual(
    values = figure_s16_colors, drop = FALSE,
    name = "B12 non-producer\nstrain spiked in"
  ) +
  ggplot2::facet_grid(. ~ assay_strain) +
  ggplot2::labs(
    title = "E. coli B12 assay",
    x = "B12 concentration (pM)",
    y = "OD600"
  ) +
  ggplot2::theme_bw(base_size = 8.5) +
  ggplot2::theme(
    plot.title = ggplot2::element_text(face = "bold", hjust = 0.5, size = 9.5),
    panel.grid.minor = ggplot2::element_blank(),
    strip.text = ggplot2::element_text(size = 8),
    legend.position = "right"
  )

figure_s16b <- figure_s16_data |>
  dplyr::filter(
    .data$assay_type == "Chlamy fluorescence",
    .data$assay_plate_number == 3,
    is.finite(.data$fluorescence), .data$fluorescence > 0
  ) |>
  ggplot2::ggplot(
    ggplot2::aes(
      x = b12_conc_pM, y = fluorescence,
      color = bacteria_strain_id
    )
  ) +
  ggplot2::geom_point(size = 1.05, alpha = 0.62) +
  ggplot2::geom_smooth(se = FALSE, linewidth = 0.65) +
  ggplot2::scale_x_log10(
    breaks = scales::breaks_log(n = 5),
    labels = scales::label_log()
  ) +
  ggplot2::scale_y_log10(
    breaks = scales::breaks_log(n = 5),
    labels = scales::label_log()
  ) +
  ggplot2::scale_color_manual(
    values = figure_s16_colors, drop = FALSE,
    name = "B12 non-producer\nstrain spiked in"
  ) +
  ggplot2::facet_grid(. ~ assay_strain) +
  ggplot2::labs(
    title = "Chlamydomonas B12 assay",
    x = "B12 concentration (pM)",
    y = "Fluorescence"
  ) +
  ggplot2::theme_bw(base_size = 8.5) +
  ggplot2::theme(
    plot.title = ggplot2::element_text(face = "bold", hjust = 0.5, size = 9.5),
    panel.grid.minor = ggplot2::element_blank(),
    strip.text = ggplot2::element_text(size = 8),
    legend.position = "right"
  )

figure_s16c <- figure_s16_data |>
  dplyr::filter(
    .data$assay_type == "E. coli OD600",
    .data$assay_plate_number == 2,
    .data$bacteria_strain_id == "blank",
    is.finite(.data$added_met_conc_uM),
    is.finite(.data$od600), .data$od600 > 0
  ) |>
  ggplot2::ggplot(
    ggplot2::aes(
      x = b12_conc_pM, y = od600,
      color = added_met_conc_uM,
      group = interaction(assay_strain, added_met_conc_uM)
    )
  ) +
  ggplot2::geom_point(size = 1.0, alpha = 0.58) +
  ggplot2::geom_smooth(se = FALSE, linewidth = 0.6) +
  ggplot2::scale_x_log10(
    breaks = scales::breaks_log(n = 5),
    labels = scales::label_log()
  ) +
  ggplot2::scale_y_log10() +
  ggplot2::scale_color_viridis_c(
    option = "D",
    trans = scales::pseudo_log_trans(sigma = 0.00001),
    breaks = c(0.1, 1, 10, 100),
    labels = scales::label_number(accuracy = 0.1),
    limits = c(0.02, 600),
    oob = scales::squish,
    name = "Added methionine\nconcentration (µM)"
  ) +
  ggplot2::facet_grid(. ~ assay_strain) +
  ggplot2::labs(
    title = "E. coli methionine series",
    x = "B12 concentration (pM)",
    y = "OD600"
  ) +
  ggplot2::theme_bw(base_size = 8.5) +
  ggplot2::theme(
    plot.title = ggplot2::element_text(face = "bold", hjust = 0.5, size = 9.5),
    panel.grid.minor = ggplot2::element_blank(),
    strip.text = ggplot2::element_text(size = 8),
    legend.position = "right"
  )

figure_s16d <- figure_s16_data |>
  dplyr::filter(
    .data$assay_type == "Chlamy fluorescence",
    .data$assay_plate_number == 4,
    .data$bacteria_strain_id == "blank",
    is.finite(.data$added_met_conc_uM),
    is.finite(.data$fluorescence), .data$fluorescence > 0
  ) |>
  ggplot2::ggplot(
    ggplot2::aes(
      x = b12_conc_pM, y = fluorescence,
      color = added_met_conc_uM,
      group = interaction(assay_strain, added_met_conc_uM)
    )
  ) +
  ggplot2::geom_point(size = 1.0, alpha = 0.58) +
  ggplot2::geom_smooth(se = FALSE, linewidth = 0.6) +
  ggplot2::scale_x_log10(
    breaks = scales::breaks_log(n = 5),
    labels = scales::label_log()
  ) +
  ggplot2::scale_y_log10(
    breaks = scales::breaks_log(n = 5),
    labels = scales::label_log()
  ) +
  ggplot2::scale_color_viridis_c(
    option = "D",
    trans = scales::pseudo_log_trans(sigma = 0.00001),
    breaks = c(0.1, 1, 10, 100),
    labels = scales::label_number(accuracy = 0.1),
    limits = c(0.02, 600),
    oob = scales::squish,
    name = "Added methionine\nconcentration (µM)"
  ) +
  ggplot2::facet_grid(. ~ assay_strain) +
  ggplot2::labs(
    title = "Chlamydomonas methionine series",
    x = "B12 concentration (pM)",
    y = "Fluorescence"
  ) +
  ggplot2::theme_bw(base_size = 8.5) +
  ggplot2::theme(
    plot.title = ggplot2::element_text(face = "bold", hjust = 0.5, size = 9.5),
    panel.grid.minor = ggplot2::element_blank(),
    strip.text = ggplot2::element_text(size = 8),
    legend.position = "right"
  )

figure_s16_top <- figure_s16a + figure_s16b +
  patchwork::plot_layout(widths = c(0.66, 0.34), guides = "collect")
figure_s16_bottom <- figure_s16c + figure_s16d +
  patchwork::plot_layout(widths = c(0.66, 0.34), guides = "collect")

figure_s16 <- (figure_s16_top / figure_s16_bottom) +
  patchwork::plot_layout(heights = c(1, 1)) +
  patchwork::plot_annotation(tag_levels = "A") &
  ggplot2::theme(
    legend.position = "right",
    plot.tag = ggplot2::element_text(face = "bold", size = 11)
  )

figure_s16_png <- file.path(output_dir, "FigureS16.png")
figure_s16_pdf <- file.path(output_dir, "FigureS16.pdf")
ggplot2::ggsave(
  figure_s16_png, figure_s16, width = 7.1, height = 5.12,
  dpi = 400, bg = "white"
)
ggplot2::ggsave(
  figure_s16_pdf, figure_s16, width = 7.1, height = 5.12,
  device = grDevices::cairo_pdf
)
figure_s16
```

## Figure S17

```{r assemble-figure-s17, fig.width=7.1, fig.height=4.44, out.width="100%"}
figure_s17_sample_colors <- c(
  filtrate = "#F8766D",
  total = "#7CAE00",
  uptake_0hr = "#00BFC4",
  uptake_1hr = "#C77CFF"
)
figure_s17_standard_colors <- c(
  blank = "grey35",
  HTWP4 = "#0072B2",
  OTU4908 = "#009E73",
  sic1606 = "#D55E00"
)

figure_s17 <- ggplot2::ggplot(
  figure_s17_data,
  ggplot2::aes(x = x_plot, y = fluorescence)
) +
  ggplot2::geom_point(
    data = function(dat) dplyr::filter(dat, assay_type == "standard"),
    ggplot2::aes(color = standard_bacteria_strain_id),
    size = 0.9, alpha = 0.48
  ) +
  ggplot2::geom_smooth(
    data = function(dat) dplyr::filter(dat, assay_type == "standard"),
    ggplot2::aes(color = standard_bacteria_strain_id),
    method = "loess", se = FALSE,
    linewidth = 0.65
  ) +
  ggplot2::scale_color_manual(
    values = figure_s17_standard_colors,
    breaks = names(figure_s17_standard_colors),
    name = "B12 non-producer\nstrain spiked in",
    guide = ggplot2::guide_legend(order = 1)
  ) +
  ggplot2::geom_violin(
    data = function(dat) dplyr::filter(dat, assay_type == "sample"),
    ggplot2::aes(
      fill = sample_type,
      group = interaction(sample_type, sample_volume_added)
    ),
    alpha = 0.8, linewidth = 0.5,
    scale = "width", trim = TRUE
  ) +
  ggplot2::scale_x_log10(
    breaks = c(1, 10, 100, 1000, 8000, 50000),
    labels = c("1", "10", "100", "1000", "10 µL\nsample", "30 µL\nsample")
  ) +
  ggplot2::scale_y_log10() +
  ggplot2::scale_fill_manual(
    values = figure_s17_sample_colors,
    breaks = names(figure_s17_sample_colors),
    labels = c("Filtrate", "Total", "Uptake, 0 h", "Uptake, 1 h"),
    name = "Sample type",
    guide = ggplot2::guide_legend(order = 2)
  ) +
  ggplot2::facet_wrap(
    ggplot2::vars(experiment_name, measure_time_hours),
    ncol = 2,
    labeller = ggplot2::labeller(
      experiment_name = ggplot2::label_value,
      measure_time_hours = function(x) paste0(x, " h")
    )
  ) +
  ggplot2::labs(
    title = "B12 assay standards and samples",
    x = "Adjusted B12 concentration in well (pM)",
    y = "Fluorescence"
  ) +
  ggplot2::theme_bw(base_size = 8) +
  ggplot2::theme(
    plot.title = ggplot2::element_text(face = "bold", size = 10, hjust = 0.5),
    panel.grid.minor = ggplot2::element_blank(),
    strip.text = ggplot2::element_text(size = 7),
    axis.text.x = ggplot2::element_text(angle = 0, hjust = 0.5),
    legend.position = "right",
    legend.key.height = grid::unit(0.8, "lines"),
    legend.key.width = grid::unit(1.0, "lines"),
    plot.margin = ggplot2::margin(4, 4, 4, 4)
  )

figure_s17_png <- file.path(output_dir, "FigureS17.png")
figure_s17_pdf <- file.path(output_dir, "FigureS17.pdf")
ggplot2::ggsave(
  figure_s17_png, figure_s17, width = 7.1, height = 4.44,
  dpi = 400, bg = "white"
)
ggplot2::ggsave(
  figure_s17_pdf, figure_s17, width = 7.1, height = 4.44,
  device = grDevices::cairo_pdf
)
figure_s17
```

```{r figures2-5-output-summary}
figure_outputs <- c(
  figure2_png, figure2_pdf,
  figure3_png, figure3_pdf,
  figure4_png, figure4_pdf,
  figure5_png, figure5_pdf,
  figure5v2_png, figure5v2_pdf,
  figure_s1_png, figure_s1_pdf,
  figure_s2_png, figure_s2_pdf,
  figure_s3_png, figure_s3_pdf,
  figure_s4_png, figure_s4_pdf,
  figure_s5_png, figure_s5_pdf,
  figure_s6_png, figure_s6_pdf,
  figure_s7_png, figure_s7_pdf,
  figure_s8_png, figure_s8_pdf,
  figure_s9_png, figure_s9_pdf,
  figure_s10_png, figure_s10_pdf,
  figure_s11_png, figure_s11_pdf,
  figure_s12_png, figure_s12_pdf,
  figure_s13_png, figure_s13_pdf,
  figure_s14_png, figure_s14_pdf,
  figure_s15_png, figure_s15_pdf,
  figure_s16_png, figure_s16_pdf,
  figure_s17_png, figure_s17_pdf
)
data.frame(
  output = figure_outputs,
  exists = file.exists(figure_outputs),
  size_bytes = file.info(figure_outputs)$size,
  row.names = NULL
)
```
